---
title: "Variability Check GMDD - part 2"
author: "Irene Xu"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: yeti
    code_folding: hide
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: true
      smooth_scroll: false
---
# 1. Load packages, Import data, Set style
```{r, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 10, fig.height = 20)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(Rmisc)
library(ggpubr)
library(EnvStats)

df_long <- read_csv("data/GMDD_TMB_long_2021-08-17.csv") %>%
  filter(!(visit %in% c("3t_mri", "4t_mri"))) %>%
  mutate(visit = as.numeric(visit))
```

***

# 2. Create functions
1. The first function plots a distribution histogram for each variable.
```{r score_bar}
score_bar <- function(data, var, vtitle, w = 1, a = 0.8) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = var, fill = arm)) + 
    geom_histogram(position = 'dodge2', alpha = a, binwidth = w) +
    theme_minimal() +
    labs(x = "", title = vtitle)
}
```

2. The second function plots the values by group.
```{r score_by_group}
score_group <- function(data, var, vtitle, s = 4, a = 0.6) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = arm, y = var, color = arm)) + 
    geom_jitter(size = s, alpha = a) +
    theme_bw() +
    theme(legend.position = "none") +
    labs(x = "", y = "", title = vtitle) +
    stat_n_text() 
}
```

3. The third function plots the values by group for each visit.
```{r score_by_visit}
score_by_visit <- function(data, var, vtitle, s = 0.5, a = 0.5) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = arm, y = var, color = arm)) + 
    geom_jitter(size = s, alpha = a) +
    theme_bw() +
    theme(legend.position = "none") +
    labs(title = vtitle, x = "", y = "") +
    stat_n_text(size = 2.8, vjust = -0.1) +
    facet_wrap(~visit, scales = "free")
}
```

4. The fourth function creates a line graph for each individual.
```{r plot_within}
plot_within <- function (data, fun.y, vtitle) {
  data$fun.y <- data[, fun.y]
  data$fun.y <- unlist(data$fun.y)
  ggplot(data, aes(as.numeric(visit), fun.y, group = record_id, color = record_id)) +
    geom_line(alpha = 0.6) +
    theme_bw() +
    theme(legend.position = "None") +
    labs(title = vtitle, subtitle = "by individial", x = "visit", y = "") +
    stat_n_text(size = 3, check_overlap = TRUE, angle = 25) 
}
```

5. The fifth function plots the mean for each visit for each group.
```{r trend_by_group}
trend_by_group <- function(data, fun.y, vtitle) {
  data$fun.y <- unlist(data[, fun.y])
  summary <- summarySE(data, measurevar = fun.y, groupvars = c("arm", "visit"), na.rm = TRUE)
  summary$fun.y = unlist(summary[, fun.y])
  ggplot(summary, aes(x = visit, y = fun.y, color = arm)) +
    geom_errorbar(aes(ymin = fun.y - se, ymax = fun.y + se), width = 0.4)+
    geom_line(position = position_dodge(-0.2)) +
    geom_point(size = 1.6, shape = 21, fill = "white", position = position_dodge(-0.2)) +
    labs(y = "", title = vtitle, subtitle = "by group") +
    theme_bw()
}
```

6. The sixth function plots the error bars for within-person variance by visit.
```{r within_by_visit}
plot_trend <- function(data, fun.y, vtitle) {
  data$fun.y <- unlist(data[, fun.y])
  SE_controlled <- summarySEwithin(data, measurevar = fun.y, 
                                   withinvars = "visit", idvar = "record_id", na.rm = TRUE)
  
  SE_controlled$fun.y = unlist(SE_controlled[, fun.y])
  
  ggplot(SE_controlled, aes(x = as.numeric(visit), y = fun.y)) +
    geom_line(color = "darkgrey") +
    geom_errorbar(aes(ymin = fun.y - se, ymax = fun.y + se), width = 0.4, color = "deepskyblue3") +
    geom_point(size = 2, shape = 21, color = "deepskyblue3", fill = "deepskyblue3") + 
    theme_bw(base_size = 12) +
    xlab("visit") +
    ylab("score") +
    ggtitle(vtitle, subtitle = "controlled for between-subject variance") +
    theme(legend.position = "none")
}
```

7. The seventh function takes in a helper function that returns the overall sd for a variable, plots the distribution of within-subject sd and plots the overall sd.
```{r plot_within_sd}
sd_all <- function(data, var) {
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd(data$var, na.rm = TRUE)
}

plot_within_sd <- function(data, var, vtitle) {
  sd_var <- sd_all(data, var)
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd_within_data <- data %>% group_by(record_id) %>% dplyr::summarize(sd = sd(var, na.rm = TRUE))
  ggplot(sd_within_data, aes(sd)) + geom_density(color = "deepskyblue4", fill = "deepskyblue4", alpha = 0.7) +
    geom_vline(data = data, xintercept = sd_var, color = "deepskyblue4") +
    theme_minimal() +
    labs(title = vtitle, subtitle = "area: within-person sd\nvertical line: within+between sd") 
}
```

8. The eighth function shows all 7 plots for each variable
```{r master-function}
plot_all <- function(var, vtitle, p1_width = 1, p1_alpha = 0.8, p2_size = 4, p2_alpha = 0.6, p3_size = 0.5, p3_alpha = 0.5) {
p1 <- score_bar(df_long, var, vtitle, p1_width, p1_alpha)
p2 <- score_group(df_long, var, vtitle, p2_size, p2_alpha)
p3 <- score_by_visit(df_long, var, vtitle, p3_size, p3_alpha)
p4 <- trend_by_group(df_long, var, vtitle)
p5 <- plot_trend(df_long, var, vtitle)
p6 <- plot_within(df_long, var, vtitle)
p7 <- plot_within_sd(df_long, var, vtitle)
lay <- rbind(c(1, 1, 1, 1, 1, 1, 2, 2, 2, 2),
             c(3, 3, 3, 3, 3, 3, 3, 3, 3, NA),
             c(3, 3, 3, 3, 3, 3, 3, 3, 3, NA),
             c(4, 4, 4, 4, 4, 5, 5, 5, 5, 5),
             c(6, 6, 6, 6, 6, 6, 7, 7, 7, 7))
grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix = lay)
}
```

***

# 3. Visualize the distribution of test scores

***
## **Test 18. CGI-S** looks good
* Clinical Global Impression: Severity
* 1, 3, 5, 7, 9, 11, 13
* variables: 1

***
T18v1.   

### **CGI-S**
```{r cgis-plots-1 }
plot_all("cgi_s", "CGI-S", 1, 0.8, 2.5, 0.25)
```

***

## **Test 19. CIRS-G** Identifiers of valid 0?
* Cumulative Illness Rating Scale - Geriatrics
* 1, 5, 9, 13
* variables: 4

***
T19v1.   

### **CIRS-G: Total**
```{r cirsg-plots-1 }
plot_all("cirsg_total_score", "CIRS-G: Total", 1, 1, 2.5, 0.25)
```

***
T19v2.   

### **CIRS-G: Severity Index**
```{r cirsg-plots-2 }
plot_all("cirsg_severity_index", "CIRS-G: Severity Index", 1, 0.8, 2.5, 0.25)
```

***
T19v3.   

### **CIRS-G: Level 3 severity**
```{r cirsg-plots-3 }
plot_all("cirsg_level3_severity", "CIRS-G: Level 3 severity", 1, 0.8, 2.5, 0.25)
```

***
T19v4.   

### **CIRS-G: Level 4 severity**
```{r cirsg-plots-4 }
plot_all("cirsg_level4_severity", "CIRS-G: Level 4 severity", 1, 0.8, 2, 0.25)
```

***

## **Test 20. SRFPC** checked
* Stroke Risk Factor Prediction Chart
* 1, 5, 9, 13
* variables: 1

***
T20v1.   

### **SRFPC: Total**
```{r srfpc-plots-1 }
plot_all("srfpc_total", "SRFPC: Total", 1, 0.8, 3, 0.3)
```

***
## **Test 21. Social Perception** checked
* Social Perception
* Mood: 1, 5, 9, 13, ...
* Control: 1, 3, 4, 5, 6, 8
* variables: 3

***
T21v1.   

### **Social Perception: Affect Naming (Total)**
```{r sp-plots-1 }
plot_all("affect_naming_total", "Social Perception: Affect Naming (Total)", 1, 0.9, 3, 0.3)
```

***
T21v2.   

### **Social Perception: Affect Naming (Scaled)**
```{r sp-plots-2 }
plot_all("affect_naming_scaled", "Social Perception: Affect Naming (Scaled)", 1, 0.9, 3, 0.3)
```

***
T21v3.   

### **Social Perception: Affect Naming (t value)**
```{r sp-plots-3 }
plot_all("affect_naming_t", "Social Perception: Affect Naming (t value)", 3, 0.9, 3, 0.3)
```

***

## **Test 22. CERAD Neuropsych Battery (Mood only)** few data?
* Social Perception
* 1, 5, 9, 13, ...
* variables: 4

***
T22v1.   

### **CERAD:  BNT Boston Naming test Total**
```{r cerad-plots-1 }
plot_all("cerad_bnt_total", "BNT Total", 0.8, 0.9, 3, 0.3)
```

***
T22v2.   

### **CERAD: Constructional Praxis Total**
```{r cerad-plots-2 }
plot_all("cerad_cp_total", "Constructional Praxis Total", 0.8, 0.9, 3, 0.3)
```

***
T22v3.   

### **CERAD: Word List Recognition Total**
```{r cerad-plots-3 }
plot_all("cerad_wlrec_total", "Word List Recognition Total", 0.8, 0.9, 3, 0.4)
```

***
T22v4.   

### **CERAD: Constructional Praxis Recall Total**
```{r cerad-plots-4 }
plot_all("cerad_cpr_total", "Constructional Praxis Recall Total", 0.5, 0.9, 3, 0.4)
```

*** 

## **Test 23. Go-No Go (Mood only)** few data?
* Go-No Go
* 1, 5, 9, 13
* variables: 2 
* Scoring: 1-More than 2 errors, 2-one to two errors, 3-no error

***
T23v1.

### **GNG: Conflict**
```{r gng-plots-1}
plot_all("gng_conflict", "GNG: Conflict", 1, 0.9, 2.5, 0.3)
```

***
T23v2.

### **GNG: Inhibit**
```{r gng-plots-2}
plot_all("gng_inhibit", "GNG: Inhibit", 1, 0.9, 2.5, 0.3)
```

*** 
## **Test 24. PANAS** checked
* Positive And Negative Affect Schedule
* all visits
* variables: 2

***
T24v1.   

### **PANAS: Positive**
```{r panas-plots-1 }
plot_all("panas_positive", "PANAS: Positive", 1, 0.9, 2.5, 0.3)
```

***
T24v2.   

### **PANAS: Negative**
```{r panas-plots-2 }
plot_all("panas_negative", "PANAS: Negative", 1, 0.9, 2.5, 0.3)
```

*** 

## **Test 25. GDS** Identifiers of valid 0?
* Geriatric Depression Scale
* all visits
* variables: 1

***
T25v1.   

### **GDS: Total** Identifiers of valid 0?
```{r gds-plots-1 }
plot_all("gds_total", "GDS: Total", 1, 0.9, 2.5, 0.25)
```

*** 

## **Test 26. GAD-7** Identifiers of valid 0?
* Geriatric Depression Scale
* all visits
* variables: 2

***
T26v1.   

### **GAD-7: Total**
```{r gad-plots-1 }
plot_all("gad_total", "GAD: Total", 1, 0.9, 2.5, 0.25)
```

***
T26v2.   

### **GAD-7: Difficulty**
```{r gad-plots-2 }
plot_all("gad_difficulty", "GAD: Difficulty", 1, 0.9, 2.5, 0.25)
```

*** 

## **Test 27. WHODAS** outlier?
* WHODAS
* 1, 3, 5, 7, 9, 11, 13
* variables: 1

***
T27v1.   

### **WHODAS: sum**
```{r whodas-plots-1}
plot_all("whodas_s_sum", "WHODAS: Sum", 1, 0.8, 2.5, 0.25)
```

*** 

## **Test 28. FAST-ER** Identifiers of valid 0?
* FAST-ER
* all visits
* variables: 1

***
T28v1.   

### **FAST-ER: Total**
```{r faster-plots-1}
plot_all("faster_total", "FAST-ER: Total", 1.5, 0.9, 2, 0.2)
```

*** 

## **Test 29. FAS-D** gap?
* Fatigue Associated with Depression
* all visits
* variables: 3

***
T29v1.   

### **FAS-D: Total **
```{r fasd-plots-1}
plot_all("fasd_total", "FAS-D: Total",1, 0.9, 2, 0.2)
```

***
T29v2.   

### **FAS-D: Total Experience**
```{r fasd-plots-2}
plot_all("fasd_total_experience", "FAS-D: Total Experience",1, 0.9, 2, 0.2)
```

***
T29v3.   

### **FAS-D: Total Impact**
```{r fasd-plots-3}
plot_all("fasd_total_impact", "FAS-D: Total Impact",1, 0.9, 2, 0.25)
```

*** 

## **Test 30. Spirituality** outliers?
* Spirituality
* 1, 3, 5, 7, 9, 11, 13
* variables: 6

***
T30v1.   

### **Spirituality I: Total**
```{r spirituality-plots-1}
plot_all("spirituality_i_total", "Spirituality I: Total", 1, 0.9, 2, 0.3)
```

***
T30v2.   

### **Spirituality II: Trust**
```{r spirituality-plots-2}
plot_all("spirituality_ii_trust", "Spirituality II: Trust", 1, 0.9, 2, 0.3)
```

***
T30v3.   

### **Spirituality II: Mistrust**
```{r spirituality-plots-3}
plot_all("spirituality_ii_mistrust", "Spirituality II: Mistrust", 1, 0.9, 2, 0.3)
```

***
T30v4.   

### **Spirituality III: Total**
```{r spirituality-plots-4}
plot_all("spirituality_iii_total", "Spirituality III: Total", 1, 0.9, 2, 0.3)
```

***
T30v5.   

### **Spirituality IV: Positive**
```{r spirituality-plots-5}
plot_all("spitituality_iv_positive", "Spirituality IV: Positive", 1, 0.9, 2, 0.3)
```

***
T30v6.   

### **Spirituality IV: Negative**
```{r spirituality-plots-6}
plot_all("spitituality_iv_negative", "Spirituality IV: Negative", 1, 0.9, 2, 0.3)
```

***

## **Test 31. GAS** Identifiers of valid 0?
* Geriatric Anxiety Scale
* all visits
* variables: 4

***
T31v1.   

### **GAS: Total**
```{r gas-plots-1}
plot_all("gas_total", "GAS: Total", 1, 0.9, 2, 0.2)
```

***
T31v2.   

### **GAS: Somatic**
```{r gas-plots-2}
plot_all("gas_somatic", "GAS: Somatic", 1, 0.9, 2, 0.2)
```

***
T31v3.   

### **GAS: Cognitive**
```{r gas-plots-3}
plot_all("gas_cognitive", "GAS: Cognitive", 1, 0.9, 2, 0.2)
```

***
T31v4.

### **GAS: Affective**
```{r gas-plots-4}
plot_all("gas_affective", "GAS: Affective", 1, 0.9, 2, 0.2)
```

*** 

## **Test 32. PSQI** cluster? Identifiers of valid 0?
* Pittsburgh Sleep Quality Index
* all visits
* variables: 1

***
T32v1.   

### **PSQI: Total**
```{r psqi-plots-1}
plot_all("psqi_global_score", "PSQI: Total", 1, 0.9, 2, 0.2)
```

*** 

## **Test 33. PAI SCZ** checked
* Personality Assessment Psychosis Subscale
* 1, 5, 9, 13
* variables: 4

***
T33v1.   

### **PAI SCZ: Total (t value)**
```{r paiscz-plots-1}
plot_all("pai_scz_total_t", "PAI SCZ: Total (t value)", 2, 0.9, 2.8, 0.25)
```

***
T33v2.   

### **PAI SCZ: Psychotic Experiences (t value)**
```{r paiscz-plots-2}
plot_all("pai_scz_psychexp_t", "PAI SCZ: Psychotic Experiences (t value)", 3, 0.9, 2.5, 0.25)
```

***
T33v3.   

### **PAI SCZ: Thought Disorder (t value)**
```{r paiscz-plots-3}
plot_all("pai_scz_thought_t", "PAI SCZ: Thought Disorder (t value)", 3, 0.9, 3, 0.3)
```

***
T33v4.   

### **PAI SCZ: Social Detachment (t value)**
```{r paiscz-plots-4}
plot_all("pai_scz_social_t", "PAI SCZ: Social Detachment (t value)", 3, 0.9, 3, 0.3)
```

*** 

## **Test 34. MMQ** gap?
* Multi-factorial Memory Questionnaire
* 1, 5, 9, 13
* variables: 1

***
T34v1.   

### **MMQ: Total**
```{r mmq-plots-1}
plot_all("mmq_total", "MMQ: Total", 2, 0.9, 2.5, 0.25)
```