---
title: "Variability Check (part 1)"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: yeti
    code_folding: hide
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: false
      smooth_scroll: true
---
# 1. Load packages, Import data, Set style
```{r, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 5, fig.height = 4)
library(tidyverse)
library(ggplot2)
library(Rmisc)
library(ggpubr)
library(EnvStats) # show n in ggplot

df_long <- read_csv("data/GMDD_TMB_long_2021-08-17.csv") %>%
  filter(!(visit %in% c("3t_mri", "4t_mri"))) %>%
  mutate(visit = as.numeric(visit))

gmdd_long <- read_csv("data/GMDD_tidy_long_2021-08-17.csv")
```

***

# 2. Create functions
```{r score_bar}
## this function plots a distribution histogram for each variable ********
score_bar <- function(data, var, vtitle, w = 1, a = 0.8) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = var, fill = arm)) + 
    geom_histogram(position = 'dodge2', alpha = a, binwidth = w) +
    theme_minimal() +
    xlab("")  +
    ggtitle(vtitle)
}
```

```{r score_by_group}
score_group <- function(data, var, vtitle, s = 4, a = 0.6) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = arm, y = var, color = arm)) + 
    geom_jitter(size = s, alpha = a) +
    theme_bw() +
    theme(legend.position = "none") +
    labs(x = "", y = "") +
    ggtitle(vtitle) + 
    stat_n_text() 
}
```

```{r score_by_visit}
score_by_visit <- function(data, var, vtitle, s = 0.5, a = 0.5) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = arm, y = var, color = arm)) + 
    geom_jitter(size = s, alpha = a) +
    theme_minimal() +
    theme(legend.position = "none") +
    labs(x = "", y = "") +
    ggtitle(vtitle) + 
    stat_n_text(size = 2) +
    facet_wrap(~visit, scales = "free")
}
```

```{r plot_within}
## this function creates a line graph for each individual ****************
plot_within <- function (data, fun.y, vtitle) {
  data$fun.y <- data[, fun.y]
  data$fun.y <- unlist(data$fun.y)
  ggplot(data, aes(as.numeric(visit), fun.y, group = record_id, color = record_id)) +
    geom_line(alpha = 0.6) +
    theme_bw() +
    theme(legend.position = "None") +
    labs(title = vtitle)  +
    ylab("") +
    xlab("visit") + 
    stat_n_text(size = 3)
}
```

```{r plot_within_sd}
## this function returns the overall sd for a variable *****************
sd_all <- function(data, var) {
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd(data$var, na.rm = TRUE)
}

# this function plots the distribution of within-subject sd for a variable, 
# and also plots the overall sd ****************************************
plot_within_sd <- function(data, var, vtitle) {
  sd_var <- sd_all(data, var)
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd_within_data <- data %>% group_by(record_id) %>% dplyr::summarize(sd = sd(var, na.rm = TRUE))
  ggplot(sd_within_data, aes(sd)) + geom_density(color = "deepskyblue4", fill = "deepskyblue4", alpha = 0.7) +
    geom_vline(data = data, xintercept = sd_var, color = "deepskyblue4") +
    theme_minimal() +
    ggtitle(vtitle) 
}
```

```{r trend_by_group}
# this function plots the mean of a variable for each visit for each group
trend_by_group <- function(data, fun.y, vtitle) {
  data$fun.y <- unlist(data[, fun.y])
  summary <- summarySE(data, measurevar = fun.y, groupvars = c("arm", "visit"), na.rm = TRUE)
  summary$fun.y = unlist(summary[, fun.y])
  ggplot(summary, aes(x = visit, y = fun.y, color = arm)) +
    geom_errorbar(aes(ymin = fun.y - se, ymax = fun.y + se), width = 0.4)+
    geom_line(position = position_dodge(0.1)) +
    geom_point(size = 1.5, shape = 21, fill = "white") +
    labs(y = "", title = vtitle) +
    theme_bw()
}
```

```{r within_by_visit}
# this function plots the error bars for within-person variance by visit ********
plot_trend <- function(data, fun.y, vtitle) {
  data$fun.y <- unlist(data[, fun.y])
  SE_controlled <- summarySEwithin(data, measurevar = fun.y, 
                                   withinvars = "visit", idvar = "record_id", na.rm = TRUE)
  
  SE_controlled$fun.y = unlist(SE_controlled[, fun.y])
  
  ggplot(SE_controlled, aes(x = as.numeric(visit), y = fun.y, color = visit)) +
    geom_line(color = "grey") +
    geom_errorbar(aes(ymin = fun.y - se, ymax = fun.y + se), width = 0.4) +
    geom_point(size = 2) + 
    theme_bw(base_size = 12) +
    xlab("visit") +
    ylab("score") +
    ggtitle(vtitle, subtitle = "controlled for between-subject variance") +
    theme(legend.position = "none")
}
```

***
# 3. Visualize the distribution of test scores

Baseline Only:
* T1   VRT
* T9   WCST
* T10  WTAR

visits 1, 3, 5, 7, 9, 11, 13:
* T7   MMSE
* T18  CGI-S
* T30  Spirituality

all visits:
* T11  MADRS
* T12  YMRS
* T13  GAF
* T24  PANAS
* T25  GDS
* T26  GAD-7
* T28  FAST-ER
* T31  GAS
* T32  PSQI

## **Test 1. VRT** checked
* Visual Reproduction Test
* baseline only
* variables: 3

***
T1v1.   

### **Immediate Recall**
```{r vrt-plots-1}
score_bar(gmdd_long, "vrt_ir_t_score", "Visual Reproduction Test: Immediate Recall (t)", 3)
score_group(gmdd_long, "vrt_ir_t_score", "Visual Reproduction Test: Immediate Recall (t)", 4, 0.7)
```

***
T1v2.

### **Delayed Recall**
```{r vrt-plots-2}
score_bar(df_long, "vrt_dr_t_score", "Visual Reproduction Test: Delayed Recall - t", 3)
score_group(df_long, "vrt_dr_t_score", "Visual Reproduction Test: Delayed Recall - t", 3, 0.7)
```

***
T1v3. 

### **Recognition Score**
```{r vrt-plots-3}
score_bar(df_long, "vrt_rec_score", "Visual Reproduction Test: Recognition Score")
score_group(df_long, "vrt_rec_score", "Visual Reproduction Test: Recognition Score", 3, 0.6)
```

***

## **Test 2. CVLT-II**
* California Verbal Learning Test  
* Mood: 1, 5, 9, 13, 14, 15
* Control: 1, 3, 4, 5, 6, 8
* variables: 8   

***
T2v1.

### **Immediate Free Recall**
```{r cvlt-plots-1-1}
score_bar(df_long, "cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall (raw)", 3, 0.8)
score_group(df_long, "cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall (raw) within", 3, 0.4)
```

```{r cvlt-plots-1-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall (raw)")
```

```{r cvlt-plots-1-3}
trend_by_group(df_long, "cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall - by group")
plot_trend(df_long, "cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall")
plot_within(df_long, "cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall - by indivodial")
plot_within_sd(df_long, "cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall - within SD")
```

***
T2v2. 

### **Total Intrusions** outliers found
```{r cvlt-plots-2-1}
score_bar(df_long, "cvlt_total_int_t", "CVLT: Total Intrusions (t)", 5)
score_group(df_long, "cvlt_total_int_t", "CVLT: Total Intrusions (t)", 2, 0.5)
```

```{r cvlt-plots-2-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_int_t", "CVLT: Total Intrusions (t)")
```

```{r cvlt-plots-2-3}
plot_within(df_long, "cvlt_total_int_t", "CVLT: Total Intrusions (t) within")
plot_trend(df_long, "cvlt_total_int_t", "CVLT: Total Intrusions (t) trend")
plot_within_sd(df_long, "cvlt_total_int_t", "CVLT: Total Intrusions (t) within SD")
```

***
T2v3.

### **Total Intrusions (Free Recall)** outliers or valid?
```{r cvlt-plots-3-1}
score_bar(df_long, "cvlt_total_free_int_t", "CVLT: Total Intrusions, free (t)", 5)
score_group(df_long, "cvlt_total_free_int_t", "CVLT: Total Intrusions, free (t)", 2, 0.5)
```

```{r cvlt-plots-3-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_free_int_t", "CVLT: Total Intrusions, free (t)")
```

```{r cvlt-plots-3-3}
plot_within(df_long, "cvlt_total_free_int_t", "CVLT: Total Intrusions, free (t) within")
plot_trend(df_long, "cvlt_total_free_int_t", "CVLT: Total Intrusions, free (t) trend")
plot_within_sd(df_long, "cvlt_total_free_int_t", "CVLT: Total Intrusions, free (t) within SD")
```

***
T2v4.

### **Total Intrusions (Cued Recall)**
```{r cvlt-plots-4-1}
score_bar(df_long, "cvlt_total_cued_int_t", "CVLT: Total Intrusions, cued (t)", 5)
score_group(df_long, "cvlt_total_cued_int_t", "CVLT: Total Intrusions, cued (t)", 2, 0.5)
```

```{r cvlt-plots-4-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_cued_int_t", "CVLT: Total Intrusions, cued (t)")
```

```{r cvlt-plots-4-3}
plot_within(df_long, "cvlt_total_cued_int_t", "CVLT: Total Intrusions, cued (t) within")
plot_trend(df_long, "cvlt_total_cued_int_t", "CVLT: Total Intrusions, cued (t) trend")
plot_within_sd(df_long, "cvlt_total_cued_int_t", "CVLT: Total Intrusions, cued (t) within SD")
```

***
T2v5. 

### **Total Recognition Target**
```{r cvlt-plots-5-1}
score_bar(df_long, "cvlt_total_rectarget_t", "CVLT: Total Recognition Target (t)", 3)
score_group(df_long, "cvlt_total_rectarget_t", "CVLT: Total Recognition Target (t)", 2, 0.5)
```

```{r cvlt-plots-5-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_rectarget_t", "CVLT: Total Recognition Target (t)")
```

```{r cvlt-plots-5-3}
plot_within(df_long, "cvlt_total_rectarget_t", "CVLT: Total Recognition Target (t) within")
plot_trend(df_long, "cvlt_total_rectarget_t", "CVLT: Total Recognition Target (t) trend")
plot_within_sd(df_long, "cvlt_total_rectarget_t", "CVLT: Total Recognition Target (t) within SD")
```

***
T2v6. 

### **Total Recognition Intrusions**
```{r cvlt-plots-6-1}
score_bar(df_long, "cvlt_total_rec_int_t", "CVLT: Total Recognition Intrusions (t)", 4)
score_group(df_long, "cvlt_total_rec_int_t", "CVLT: Total Recognition Intrusions (t)", 2, 0.5)
```

```{r cvlt-plots-6-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_rec_int_t", "CVLT: Total Recognition Intrusions (t)")
```

```{r cvlt-plots-6-3}
plot_within(df_long, "cvlt_total_rec_int_t", "CVLT: Total Recognition Intrusions (t) within")
plot_trend(df_long, "cvlt_total_rec_int_t", "CVLT: Total Recognition Intrusions (t) trend")
plot_within_sd(df_long, "cvlt_total_rec_int_t", "CVLT: Total Recognition Intrusions (t) within SD")
```

***
T2v7. 

### **Total Recognition Accuracy** outliers found
```{r cvlt-plots-7-1}
score_bar(df_long, "cvlt_total_rec_accuracy", "CVLT: Total Recognition Accuracy (t)", 5)
score_group(df_long, "cvlt_total_rec_accuracy", "CVLT: Total Recognition Accuracy (t)", 2, 0.5)
```

```{r cvlt-plots-7-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_rec_accuracy", "CVLT: Total Recognition Accuracy (t)")
```

```{r cvlt-plots-7-3}
plot_within(df_long, "cvlt_total_rec_accuracy", "CVLT: Total Recognition Accuracy (t) within")
plot_trend(df_long, "cvlt_total_rec_accuracy", "CVLT: Total Recognition Accuracy (t) trend")
plot_within_sd(df_long, "cvlt_total_rec_accuracy", "CVLT: Total Recognition Accuracy (t) within SD")
```

***
T2v8. 

### **Total Repetition**
```{r cvlt-plots-8-1}
score_bar(df_long, "cvlt_total_rep_t", "CVLT: Total Repetition - t ", 5)
score_group(df_long, "cvlt_total_rep_t", "CVLT: Total Repetition - t ", 2, 0.5)
```

```{r cvlt-plots-8-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "cvlt_total_rep_t", "CVLT: Total Repetition (t)")
```

```{r cvlt-plots-8-3}
plot_within(df_long, "cvlt_total_rep_t", "CVLT: Total Repetition - t - within")
plot_trend(df_long, "cvlt_total_rep_t", "CVLT: Total Repetition (t) trend")
plot_within_sd(df_long, "cvlt_total_rep_t", "CVLT: Total Repetition - t - within SD")
```

***

## **Test 3. VFT**
* Verbal Fluency Test (aka. FAS)
* Mood: 1, 5, 9, 13, 14, 15
* Control: 1, 3, 4, 5, 6, 8
* variables: 2

***
T3v1.

### **Animals**
```{r vft-plots-1-1}
score_bar(df_long, "vft_animals", "VFT: Animals")
score_group(df_long, "vft_animals", "VFT: Animals", 2, 0.5)
```

```{r vft-plots-1-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "vft_animals", "VFT: Animals")
```

```{r vft-plots-1-3}
plot_within(df_long, "vft_animals", "VFT: Animals - within")
plot_trend(df_long, "vft_animals", "VFT: Animals - trend")
plot_within_sd(df_long, "vft_animals", "VFT: Animals - within SD")
```

***
T3v2.

### **FAS**
```{r vft-plots-2-1}
score_bar(df_long, "vft_fas_raw", "VFT: FAS (raw)")
score_group(df_long, "vft_fas_raw", "VFT: FAS (raw)", 2, 0.4)
```

```{r vft-plots-2-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "vft_fas_raw", "VFT: FAS (raw)")
```

```{r vft-plots-2-3}
plot_within(df_long, "vft_fas_raw", "VFT: FAS (raw) - within")
plot_trend(df_long, "vft_fas_raw", "VFT: FAS (raw) - trend")
plot_within_sd(df_long, "vft_fas_raw", "VFT: FAS - raw - within SD")
```

***

## **Test 4. Stroop**
* Stroop Test
* Mood: 1, 5, 9, 13, 14, 15
* Control: 1, 3, 4, 5, 6, 8
* variables: 4

***
T4v1.

### **Word Deviation** how to identify valid scores or 0?
```{r stroop-plots-1-1}
score_bar(df_long, "stroop_wscore_dev", "Stroop: word deviation")
score_group(df_long, "stroop_wscore_dev", "Stroop: word deviation", 2, 0.4)
```

```{r stroop-plots-1-2, fig.width = 7, fig.height = 7}
score_by_visit(df_long, "stroop_wscore_dev", "Stroop: word deviation")
```

```{r stroop-plots-1-3}
plot_within(df_long, "stroop_wscore_dev", "Stroop: word deviation - by individual")
trend_by_group(df_long, "stroop_wscore_dev", "Stroop: word deviation")
plot_trend(df_long, "stroop_wscore_dev", "Stroop: word deviation - trend")
plot_within_sd(df_long, "stroop_wscore_dev", "Stroop: word deviation - within SD")
```

***
T4v2.

### **Color Deviation**
```{r stroop-plots-2}
score_bar(df_long, "stroop_cscore_dev", "Stroop: color deviation")
plot_within(df_long, "stroop_cscore_dev", "Stroop: color deviation - within")
plot_trend(df_long, "stroop_cscore_dev", "Stroop: color deviation - trend")
plot_within_sd(df_long, "stroop_cscore_dev", "Stroop: color deviation - within SD")
```

***
T4v3.

### **Color Word Deviation**
```{r stroop-plots-3}
score_bar(df_long, "stroop_cwscore_dev_3", "Stroop: color word deviation")
plot_within(df_long, "stroop_cwscore_dev_3", "Stroop: color word deviation - within")
plot_trend(df_long, "stroop_cwscore_dev_3", "Stroop: color word deviation - trend")
plot_within_sd(df_long, "stroop_cwscore_dev_3", "Stroop: color word deviation - within SD")
```

***
T4v4.

### **Color Word**
```{r stroop-plots-4}
score_bar(df_long, "strop_cw_int_t", "Stroop: color word (t)")
plot_within(df_long, "strop_cw_int_t", "Stroop: color word (t) - within")
plot_trend(df_long, "strop_cw_int_t", "Stroop: color word (t) - trend")
plot_within_sd(df_long, "strop_cw_int_t", "Stroop: color word (t) - within SD")
```

***

## **Test 5. Trails A+B ** (data removed from redcap)
VAR not able to download *****

***

## **Test 6. Coding**
* Coding and Symbol Search
* baseline, v5, v9, v13
* variables: 2

***
T6v1.

### **Coding t value**
```{r coding-plots-1}
score_bar(df_long, "coding_t_score", "Coding")
plot_within(df_long, "coding_t_score", "Coding - within")
plot_trend(df_long, "coding_t_score", "Coding - trend")
plot_within_sd(df_long, "coding_t_score", "Coding - within SD")
```

***
T6v2.

### **Symbol Search t value**
```{r coding-plots-2}
score_bar(df_long, "symbol_search_t", "Symbol Search")
plot_within(df_long, "symbol_search_t", "Symbol Search - within")
plot_trend(df_long, "symbol_search_t", "Symbol Search - trend")
plot_within_sd(df_long, "symbol_search_t", "Symbol Search - within SD")
```

***
T6v3.

### **Coding Score (TMB data)**
```{r coding-plots-3, eval = FALSE}
score_bar(df_long, "coding_score", "Coding Score")
plot_within(df_long, "coding_score", "Coding Score - within")
plot_trend(df_long, "coding_score", "Coding Score - trend")
plot_within_sd(df_long, "coding_score", "Coding Score - within SD")
```

***
T6v4.

### **Coding Errors (TMB data)**
```{r coding-plots-4, eval = FALSE}
score_bar(df_long, "coding_errors", "Coding Errors")
plot_within(df_long, "coding_errors", "Coding Errors - within")
plot_trend(df_long, "coding_errors", "Coding Errors - trend")
plot_within_sd(df_long, "coding_errors", "Coding Errors - within SD")
```

***
T6v5.

### **Coding Median RT (TMB data)**
```{r coding-plots-5, eval = FALSE}
score_bar(df_long, "coding_medianRT", "Coding Median RT")
plot_within(df_long, "coding_medianRT", "Coding Median RT - within")
plot_trend(df_long, "coding_medianRT", "Coding Median RT - trend")
plot_within_sd(df_long, "coding_medianRT", "Coding Median RT - within SD")
```

***
T6v6.

### **Coding sd RT (TMB data)**
```{r coding-plots-6, eval = FALSE}
score_bar(df_long, "coding_sdRT", "Coding sd RT")
plot_within(df_long, "coding_sdRT", "Coding sd RT - within")
plot_trend(df_long, "coding_sdRT", "Coding sd RT - trend")
plot_within_sd(df_long, "coding_sdRT", "Coding sd RT - within SD")
```

***
T6v7.

### **Coding timeouts (TMB data) ***** NA ******


***

## **Test 7. MMSE**
* Mini-Mental State Exam
* baseline, v3, 5, 7, 9, 11, 13
* variables: 1

***
T7v1.

### **Total**
```{r mmse-plots-1}
score_bar(df_long, "mmse_total_score", "MMSE Total")
plot_within(df_long, "mmse_total_score", "MMSE Total - within")
plot_trend(df_long, "mmse_total_score", "MMSE Total - trend")
plot_within_sd(df_long, "mmse_total_score", "NMMSE Total - within SD")
```

***

## **Test 8. Emotional Stroop** (data removed from redcap)
VAR not able to download *****
note: Not administered in any visit for the majority - why??

***

## **Test 9. WCST** (some data removed from redcap)
* Wisconsin Card Sort Task
* baseline
* variables: 20+

***
T9v1.

### **Total Error - raw**
```{r wcst-plots-1}
score_bar(df_long, "wcst_total_errors_raw", "WCST: Total Error - raw")
```

***
T9v2.

### **Total Error STD**
```{r wcst-plots-2}
score_bar(df_long, "wcst_total_errors_std", "WCST: Total Error STD")
```


***
T9v2-2.

### **Total Error STD-2**
```{r wcst-plots-2-2}
score_bar(df_long, "wcst_total_errors_std_2", "WCST: Total Error STD-2")
```

***
T9v3.

### **Total Error t**
```{r wcst-plots-3}
score_bar(df_long, "wcst_total_errors_t", "WCST: Total Error t")
```

***
T9v3-2.

### **Total Error t-2**
```{r wcst-plots-3-2}
score_bar(df_long, "wcst_total_errors_t_2", "WCST: Total Error t-2")
```

***
T9v4.

### **Total Error pct**
```{r wcst-plots-4}
score_bar(df_long, "wcst_total_errors_pct", "WCST: Total Error pct")
```

***
T9v4-2.

### **Total Error pct-2**
```{r wcst-plots-4-2}
score_bar(df_long, "wcst_total_errors_pct_2", "WCST: Total Error pct-2")
```

***
T9v5.

### **Perseverative Responses - raw**
```{r wcst-plots-5}
score_bar(df_long, "wcst_pers_res_raw", "WCST: Perseverative Responses - raw")
```

***
T9v6.

### **Perseverative Responses - STD**
```{r wcst-plots-6}
score_bar(df_long, "wcst_pers_res_std", "WCST: Perseverative Responses - std")
```

***
T9v6-2.

### **Perseverative Responses - STD-2**
```{r wcst-plots-6-2}
score_bar(df_long, "wcst_pers_res_std_2", "WCST: Perseverative Responses - std-2")
```

***
T9v7.

### **Perseverative Responses - t**
```{r wcst-plots-7}
score_bar(df_long, "wcst_pers_res_t", "WCST: Perseverative Responses - t")
```

***
T9v7-2.

### **Perseverative Responses - t-2**
```{r wcst-plots-7-2}
score_bar(df_long, "wcst_pers_res_t_2", "WCST: Perseverative Responses - t-2")
```

***
T9v8.

### **Perseverative Responses - pct**
```{r wcst-plots-8}
score_bar(df_long, "wcst_pers_res_pct", "WCST: Perseverative Responses - pct")
```

***
T9v8-2.

### **Perseverative Responses - pct-2**
```{r wcst-plots-8-2}
score_bar(df_long, "wcst_pers_res_pct_2", "WCST: Perseverative Responses - pc-2")
```

***
T9v9.

### **Perseverative Errors - raw**
```{r wcst-plots-9}
score_bar(df_long, "wcst_pers_err_pct", "WCST: Perseverative Errors - raw")
```

***
T9v10.

### **Perseverative Errors - STD**
```{r wcst-plots-10}
score_bar(df_long, "wcst_pers_err_std", "WCST: Perseverative Errors - std")
```

***
T9v10-2.

### **Perseverative Errors - STD-2**
```{r wcst-plots-10-2}
score_bar(df_long, "wcst_pers_err_std_2", "WCST: Perseverative Errors - std-2")
```

***
T9v11.

### **Perseverative Errors - t**
```{r wcst-plots-11}
score_bar(df_long, "wcst_pers_err_t", "WCST: Perseverative Errors - t")
```

***
T9v11-2.

### **Perseverative Errors - t-2**
```{r wcst-plots-11-2}
score_bar(df_long, "wcst_pers_err_t_2", "WCST: Perseverative Errors - t-2")
```

***
T9v12.

### **Perseverative Errors - pct**
```{r wcst-plots-12}
score_bar(df_long, "wcst_pers_err_pct", "WCST: Perseverative Errors - pct")
```

***
T9v12-2.

### **Perseverative Errors - pct-2**
```{r wcst-plots-12-2}
score_bar(df_long, "wcst_pers_err_pct_2", "WCST: Perseverative Errors - pct-2")
```

***
T9v13.

### **Non-Perseverative Errors - raw**
```{r wcst-plots-13}
score_bar(df_long, "wcst_npers_err_raw", "WCST: Non-Perseverative Errors - raw")
```

***
T9v14.

### **Non-Perseverative Errors - std**
```{r wcst-plots-14}
score_bar(df_long, "wcst_npers_err_std", "WCST: Non-Perseverative Errors - std")
```

***
T9v14-2.

### **Non-Perseverative Errors - std-2**
```{r wcst-plots-14-2}
score_bar(df_long, "wcst_npers_err_std_2", "WCST: Non-Perseverative Errors - std-2")
```

***
T9v15.

### **Non-Perseverative Errors - t**
```{r wcst-plots-15}
score_bar(df_long, "wcst_npers_err_t", "WCST: Non-Perseverative Errors - t")
```

***
T9v15-2.

### **Non-Perseverative Errors - t-2**
```{r wcst-plots-15-2}
score_bar(df_long, "wcst_npers_err_t_2", "WCST: Non-Perseverative Errors - t-2")
```

***
T9v16.

### **Non-Perseverative Errors - pct**
```{r wcst-plots-16}
score_bar(df_long, "wcst_npers_err_pct", "WCST: Non-Perseverative Errors - pct")
```

***
T9v16-2.

### **Non-Perseverative Errors - pct**
```{r wcst-plots-16-2}
score_bar(df_long, "wcst_npers_err_pct_2", "WCST: Non-Perseverative Errors - pct-2")
```

***
T9v17.

### **Conceptual Level Responses - raw**
```{r wcst-plots-17}
score_bar(df_long, "wcst_conc_raw", "WCST: Conceptual Level Responses - raw")
```

***
T9v18.

### **Conceptual Level Responses - std**
```{r wcst-plots-18}
score_bar(df_long, "wcst_conc_std", "WCST: Conceptual Level Responses - std")
```

***
T9v18-2.

### **Conceptual Level Responses - std-2**
```{r wcst-plots-18-2}
score_bar(df_long, "wcst_conc_std_2", "WCST: Conceptual Level Responses - std-2")
```

***
T9v19.

### **Conceptual Level Responses - t**
```{r wcst-plots-19}
score_bar(df_long, "wcst_conc_t", "WCST: Conceptual Level Responses - t")
```

***
T9v19-2.

### **Conceptual Level Responses - t-2**
```{r wcst-plots-19-2}
score_bar(df_long, "wcst_conc_t_2", "WCST: Conceptual Level Responses - t-2")
```

***
T9v20.

### **Conceptual Level Responses - pct**
```{r wcst-plots-20}
score_bar(df_long, "wcst_conc_pct", "WCST: Conceptual Level Responses - pct")
```

***
T9v20-2.

### **Conceptual Level Responses - pct-2**
```{r wcst-plots-20-2}
score_bar(df_long, "wcst_conc_pct_2", "WCST: Conceptual Level Responses - pct-2")
```

***

## **Test 10. WTAR**
* Weschler Test of Adult Reading
* baseline
* variables: 1

***
T10v1.

### **Total**
```{r wtar-plots-1}
score_bar(df_long, "wtar_raw_score", "WTAR: Total")
```

***

## **Test 11. MADRS**
* Montgomery-Asberg Depression Rating Scale
* all visits
* variables: 11

***
T11v1.

### **Total**
```{r madrs-plots-1}
score_bar(df_long, "madrs_total", "MADRS: Total")  

#p1 <- ggplot(df_long, aes(as.numeric(visit), madrs_total, group = record_id, color = record_id)) +
#    geom_line(alpha = 0.3) +
#    theme_classic(base_size = 12) +
#    theme(legend.position = "None") +
#    ylab("")
#ggplotly(p1)

plot_within(df_long, "madrs_total", "MADRS: Total - within")
plot_trend(df_long, "madrs_total", "MADRS: Total - trend")
plot_within_sd(df_long, "madrs_total", "MADRS: Total - within SD")
```

***
T11v2.

### **Apparent Sadness**
```{r madrs-plots-2}
score_bar(df_long, "madrs_as_score", "MADRS: Apparent Sadness")
plot_within(df_long, "madrs_as_score", "MADRS: Apparent Sadness - within")
plot_trend(df_long, "madrs_as_score", "MADRS: Apparent Sadness - trend")
plot_within_sd(df_long, "madrs_as_score", "MADRS: Apparent Sadness - within SD")
```

***
T11v3.

### **Reported Sadness**
```{r madrs-plots-3}
score_bar(df_long, "madrs_rs_score", "MADRS: Reported Sadness")
plot_within(df_long, "madrs_rs_score", "MADRS: Reported Sadness - within")
plot_trend(df_long, "madrs_rs_score", "MADRS: Reported Sadness - trend")
plot_within_sd(df_long, "madrs_rs_score", "MADRS: Reported Sadness - within SD")
```

***
T11v4.

### **Inner Tension**
```{r madrs-plots-4}
score_bar(df_long, "madrs_it_score", "MADRS: Inner Tension")
plot_within(df_long, "madrs_it_score", "MADRS: Inner Tension - within")
plot_trend(df_long, "madrs_it_score", "MADRS: Inner Tension - trend")
plot_within_sd(df_long, "madrs_it_score", "MADRS: Inner Tension - within SD")
```

***
T11v5.

### **Reduced Sleep**
```{r madrs-plots-5}
score_bar(df_long, "madrs_rs_score", "MADRS: Reduced Sleep")
plot_within(df_long, "madrs_rs_score", "MADRS: Reduced Sleep - within")
plot_trend(df_long, "madrs_rs_score", "MADRS: Reduced Sleep - trend")
plot_within_sd(df_long, "madrs_rs_score", "MADRS: Reduced Sleep - within SD")
```

***
T11v6.

### **Reduced Appetite**
```{r madrs-plots-6}
score_bar(df_long, "madrs_ra_score", "MADRS: Reduced Appetite")
plot_within(df_long, "madrs_ra_score", "MADRS: Reduced Appetite - within")
plot_trend(df_long, "madrs_ra_score", "MADRS: Reduced Appetite - trend")
plot_within_sd(df_long, "madrs_ra_score", "MADRS: Reduced Appetite - within SD")
```

***
T11v7.

### **Concentration Difficulties**
```{r madrs-plots-7}
score_bar(df_long, "madrs_cd_score", "MADRS: Concentration Difficulties")
plot_within(df_long, "madrs_cd_score", "MADRS: Concentration Difficulties - within")
plot_trend(df_long, "madrs_cd_score", "MADRS: Concentration Difficulties - trend")
plot_within_sd(df_long, "madrs_cd_score", "MADRS: Concentration Difficulties - within SD")
```

***
T11v8.

### **Lassitude**
```{r madrs-plots-8}
score_bar(df_long, "madrs_las_score", "MADRS: Lassitude")
plot_within(df_long, "madrs_las_score", "MADRS: Lassitude - within")
plot_trend(df_long, "madrs_las_score", "MADRS: Lassitude - trend")
plot_within_sd(df_long, "madrs_las_score", "MADRS: Lassitude - within SD")
```

***
T11v9.

### **Inability to Feel**
```{r madrs-plots-9}
score_bar(df_long, "madrs_itf_score", "MADRS: Inability to Feel")
plot_within(df_long, "madrs_itf_score", "MADRS: Inability to Feel - within")
plot_trend(df_long, "madrs_itf_score", "MADRS: Inability to Feel - trend")
plot_within_sd(df_long, "madrs_itf_score", "MADRS: Inability to Feel - within SD")
```

***
T11v10.

### **Pessimistic Thoughts**
```{r madrs-plots-10}
score_bar(df_long, "madrs_pt_score", "MADRS: Pessimistic Thoughts")
plot_within(df_long, "madrs_pt_score", "MADRS: Pessimistic Thoughts - within")
plot_trend(df_long, "madrs_pt_score", "MADRS: Pessimistic Thoughts - trend")
plot_within_sd(df_long, "madrs_pt_score", "MADRS: Pessimistic Thoughts - within SD")
```

***
T11v11.

### **Suicidal Thoughts**
```{r madrs-plots-11}
score_bar(df_long, "madrs_st_score", "MADRS: Suicidal Thoughts")
plot_within(df_long, "madrs_st_score", "MADRS: Suicidal Thoughts - within")
plot_trend(df_long, "madrs_st_score", "MADRS: Suicidal Thoughts - trend")
plot_within_sd(df_long, "madrs_st_score", "MADRS: Suicidal Thoughts - within SD")
```


***

## **Test 12. YMRS**
* Young Mania Rating Scale
* all visits
* variables: 12

***
T12v1.

### **Total**
```{r ymrs-plots-1}
score_bar(df_long, "ymrs_total", "YMRS: Total")  
plot_within(df_long, "ymrs_total", "YMRS: Total - within")
plot_trend(df_long, "ymrs_total", "YMRS: Total - trend")
plot_within_sd(df_long, "ymrs_total", "YMRS: Total - within SD")
```

***
T12v2.

### **Elevated Mood**
```{r ymrs-plots-2}
score_bar(df_long, "ymrs_elevatedmood", "YMRS: Elevated Mood")  
plot_within(df_long, "ymrs_elevatedmood", "YMRS: Elevated Mood - within")
plot_trend(df_long, "ymrs_elevatedmood", "YMRS: Elevated Mood - trend")
plot_within_sd(df_long, "ymrs_elevatedmood", "YMRS: Elevated Mood - within SD")
```

***
T12v3.

### **Motor Activity**
```{r ymrs-plots-3}
score_bar(df_long, "ymrs_motoractivity", "YMRS: Motor Activity")  
plot_within(df_long, "ymrs_motoractivity", "YMRS: Motor Activity - within")
plot_trend(df_long, "ymrs_motoractivity", "YMRS: Motor Activity - trend")
plot_within_sd(df_long, "ymrs_motoractivity", "YMRS: Motor Activity - within SD")
```

***
T12v4.

### **Sex Interest**
```{r ymrs-plots-4}
score_bar(df_long, "ymrs_sexinterest", "YMRS: Sex Interest")  
plot_within(df_long, "ymrs_sexinterest", "YMRS: Sex Interest - within")
plot_trend(df_long, "ymrs_sexinterest", "YMRS: Sex Interest - trend")
plot_within_sd(df_long, "ymrs_sexinterest", "YMRS: Sex Interest - within SD")
```

***
T12v5.

### **Sleep**
```{r ymrs-plots-5}
score_bar(df_long, "ymrs_sleep", "YMRS: Sleep")  
plot_within(df_long, "ymrs_sleep", "YMRS: Sleep - within")
plot_trend(df_long, "ymrs_sleep", "YMRS: Sleep - trend")
plot_within_sd(df_long, "ymrs_sleep", "YMRS: Sleep - within SD")
```

***
T12v6.

### **Irritability**
```{r ymrs-plots-6}
score_bar(df_long, "ymrs_irritability", "YMRS: Irritability")  
plot_within(df_long, "ymrs_irritability", "YMRS: Irritability - within")
plot_trend(df_long, "ymrs_irritability", "YMRS: Irritability - trend")
plot_within_sd(df_long, "ymrs_irritability", "YMRS: Irritability - within SD")
```
***

T12v7.

### **Speech**
```{r ymrs-plots-7}
score_bar(df_long, "ymrs_speech", "YMRS: Speech")  
plot_within(df_long, "ymrs_speech", "YMRS: Speech - within")
plot_trend(df_long, "ymrs_speech", "YMRS: Speech - trend")
plot_within_sd(df_long, "ymrs_speech", "YMRS: Speech - within SD")
```

***
T12v8.

### **Language**
```{r ymrs-plots-8}
score_bar(df_long, "ymrs_language", "YMRS: Language")  
plot_within(df_long, "ymrs_language", "YMRS: Language - within")
plot_trend(df_long, "ymrs_language", "YMRS: Language - trend")
plot_within_sd(df_long, "ymrs_language", "YMRS: Language - within SD")
```

***
T12v9.

### **Content**
```{r ymrs-plots-9}
score_bar(df_long, "ymrs_content", "YMRS: Content")  
plot_within(df_long, "ymrs_content", "YMRS: Content - within")
plot_trend(df_long, "ymrs_content", "YMRS: Content - trend")
plot_within_sd(df_long, "ymrs_content", "YMRS: Content - within SD")
```

***
T12v10.

### **Disruptive**
```{r ymrs-plots-10}
score_bar(df_long, "ymrs_disruptive", "YMRS: Disruptive")  
plot_within(df_long, "ymrs_disruptive", "YMRS: Disruptive - within")
plot_trend(df_long, "ymrs_disruptive", "YMRS: Disruptive - trend")
plot_within_sd(df_long, "ymrs_disruptive", "YMRS: Disruptive - within SD")
```

***
T12v11.

### **Appearance**
```{r ymrs-plots-11}
score_bar(df_long, "ymrs_appearance", "YMRS: Appearance")  
plot_within(df_long, "ymrs_appearance", "YMRS: Appearance - within")
plot_trend(df_long, "ymrs_appearance", "YMRS: Appearance - trend")
plot_within_sd(df_long, "ymrs_appearance", "YMRS: Appearance - within SD")
```

***
T12v12.

### **Insight**
```{r ymrs-plots-12}
score_bar(df_long, "ymrs_insight", "YMRS: Insight")  
plot_within(df_long, "ymrs_insight", "YMRS: Insight - within")
plot_trend(df_long, "ymrs_insight", "YMRS: Insight - trend")
plot_within_sd(df_long, "ymrs_insight", "YMRS: Insight - within SD")
```

***

## **Test 13. GAF**
* Global Assessment of Functioning
* all visits
* variables: 1

***
T13v1.

### **Score**
```{r gaf-plots-1}
score_bar(df_long, "gaf_score", "GAF: Score")  
plot_within(df_long, "gaf_score", "GAF: Score - within")
plot_trend(df_long, "gaf_score", "GAF: Score - trend")
plot_within_sd(df_long, "gaf_score", "GAF: Score - within SD")
```

***

## **Test 14. IGT**
* Iowa Gambling Task
* baseline, 5, 9, 13
* variables: 11

***
T14v1.

### **Net Total**
```{r igt-plots-1}
score_bar(df_long, "igt_net_total_t", "IGT: Net Total (t)")  
plot_within(df_long, "igt_net_total_t", "IGT: Net Total (t) - within")
plot_trend(df_long, "igt_net_total_t", "IGT: Net Total (t) - trend")
plot_within_sd(df_long, "igt_net_total_t", "IGT: Net Total (t) - within SD")
```

***
T14v2.

### **Net part 1 (t value)**
```{r igt-plots-2}
score_bar(df_long, "igt_net_1_t", "IGT: Net part 1 (t)")  
plot_within(df_long, "igt_net_1_t", "IGT: Net part 1 (t) - within")
plot_trend(df_long, "igt_net_1_t", "IGT: Net part 1 (t) - trend")
plot_within_sd(df_long, "igt_net_1_t", "IGT: Net part 1 (t) - within SD")
```

***
T14v3.

### **Net part 2 (t value)**
```{r igt-plots-3}
score_bar(df_long, "igt_net_2_t", "IGT: Net part 2 (t)")  
plot_within(df_long, "igt_net_2_t", "IGT: Net part 2 (t) - within")
plot_trend(df_long, "igt_net_2_t", "IGT: Net part 2 (t) - trend")
plot_within_sd(df_long, "igt_net_2_t", "IGT: Net part 2 (t) - within SD")
```

***
T14v4.

### **Net part 3 (t value)**
```{r igt-plots-4}
score_bar(df_long, "igt_net_3_t", "IGT: Net part 3 (t)")  
plot_within(df_long, "igt_net_3_t", "IGT: Net part 3 (t) - within")
plot_trend(df_long, "igt_net_3_t", "IGT: Net part 3 (t) - trend")
plot_within_sd(df_long, "igt_net_3_t", "IGT: Net part 3 (t) - within SD")
```

***
T14v5.

### **Net part 4 (t value)**
```{r igt-plots-5}
score_bar(df_long, "igt_net_4_t", "IGT: Net part 4 (t)")  
plot_within(df_long, "igt_net_4_t", "IGT: Net part 4 (t) - within")
plot_trend(df_long, "igt_net_4_t", "IGT: Net part 4 (t) - trend")
plot_within_sd(df_long, "igt_net_4_t", "IGT: Net part 4 (t) - within SD")
```

***
T14v6.

### **Net part 5 (t value)**
```{r igt-plots-6}
score_bar(df_long, "igt_net_5_t", "IGT: Net part 5 (t)")  
plot_within(df_long, "igt_net_5_t", "IGT: Net part 5 (t) - within")
plot_trend(df_long, "igt_net_5_t", "IGT: Net part 5 (t) - trend")
plot_within_sd(df_long, "igt_net_5_t", "IGT: Net part 5 (t) - within SD")
```

***
T14v7.

### **Deck A**
```{r igt-plots-7}
score_bar(df_long, "igt_deck_a", "IGT: Deck A")  
plot_within(df_long, "igt_deck_a", "IGT: Deck A - within")
plot_trend(df_long, "igt_deck_a", "IGT: Deck A - trend")
plot_within_sd(df_long, "igt_deck_a", "IGT: Deck A - within SD")
```

***
T14v8.

### **Deck B**
```{r igt-plots-8}
score_bar(df_long, "igt_deck_b", "IGT: Deck B")  
plot_within(df_long, "igt_deck_b", "IGT: Deck B - within")
plot_trend(df_long, "igt_deck_b", "IGT: Deck B - trend")
plot_within_sd(df_long, "igt_deck_b", "IGT: Deck B - within SD")
```

***
T14v9.

### **Deck C**
```{r igt-plots-9}
score_bar(df_long, "igt_deck_c", "IGT: Deck C")  
plot_within(df_long, "igt_deck_c", "IGT: Deck C - within")
plot_trend(df_long, "igt_deck_c", "IGT: Deck C - trend")
plot_within_sd(df_long, "igt_deck_c", "IGT: Deck C - within SD")
```

***
T14v10.

### **Deck D**
```{r igt-plots-10}
score_bar(df_long, "igt_deck_d", "IGT: Deck D")  
plot_within(df_long, "igt_deck_d", "IGT: Deck D - within")
plot_trend(df_long, "igt_deck_d", "IGT: Deck D - trend")
plot_within_sd(df_long, "igt_deck_d", "IGT: Deck D - within SD")
```

***
T14v11.

### **Total money**
```{r igt-plots-11}
score_bar(df_long, "igt_total_money", "IGT: Total money")  
plot_within(df_long, "igt_total_money", "IGT: Total money - within")
plot_trend(df_long, "igt_total_money", "IGT: Total money - trend")
plot_within_sd(df_long, "igt_total_money", "IGT: Total money - within SD")
```

***

## **Test 15. VOSP**
* Visual Object and Space Perception: Shape Detection
* baseline, 5, 9, 13
* variables: 1

***
T15v1.

### **Total**
```{r vosp-plots-1}
score_bar(df_long, "vosp_total", "VOSP: Total")  
plot_within(df_long, "vosp_total", "VOSP: Total - within")
plot_trend(df_long, "vosp_total", "VOSP: Total - trend")
plot_within_sd(df_long, "vosp_total", "VOSP: Total - within SD")
```

***

## **Test 16. MITE**
* Mind in the Eyes
* baseline, 5, 9, 13
* variables: 2

***
T16v1.

### **Correct**
```{r mite-plots-1}
score_bar(df_long, "mind_eyes_correct", "MITE: Correct")  
plot_within(df_long, "mind_eyes_correct", "MITE: Correct - within")
plot_trend(df_long, "mind_eyes_correct", "MITE: Correct - trend")
plot_within_sd(df_long, "mind_eyes_correct", "MITE: Correct - within SD")
```

***
T16v2.

### **t - value**
```{r mite-plots-2}
score_bar(df_long, "mind_eyes_t", "MITE: t value")  
plot_within(df_long, "mind_eyes_t", "MITE: t value - within")
plot_trend(df_long, "mind_eyes_t", "MITE: t value - trend")
plot_within_sd(df_long, "mind_eyes_t", "MITE: t value - within SD")
```

***

## **Test 17. TMB** (not added yet)
* Test My Brain
* baseline, 5, 9, 13
* variables: 4 

***
T17v1.

### **TMB: Response Speed Score**
```{r tmb-plots-1, eval=FALSE}
score_bar(df_long, "response_speed_score", "TMB: Response Speed Score")  
plot_within(df_long, "response_speed_score", "TMB: Response Speed Score - within")
plot_trend(df_long, "response_speed_score", "TMB: Response Speed Score - trend")
plot_within_sd(df_long, "response_speed_score", "TMB: Response Speed Score - within SD")
```

### **TMB: Response Speed RT**
```{r tmb-plots-1, eval=FALSE}
score_bar(df_long, "response_speed_score", "TMB: Response Speed Score")  
plot_within(df_long, "response_speed_score", "TMB: Response Speed Score - within")
plot_trend(df_long, "response_speed_score", "TMB: Response Speed Score - trend")
plot_within_sd(df_long, "response_speed_score", "TMB: Response Speed Score - within SD")
```

***
T17v2.

### **TMB: Fast choices**
```{r tmb-plots-2, eval=FALSE}
score_bar(df_long, "tmb_fast_choices", "TMB: Fast choices")  
plot_within(df_long, "tmb_fast_choices", "TMB: Fast choices - within")
plot_trend(df_long, "tmb_fast_choices", "TMB: Fast choices - trend")
plot_within_sd(df_long, "tmb_fast_choices", "TMB: Fast choices - within SD")
```

***
T17v3.

### **TMB: Matching**
```{r tmb-plots-3, eval=FALSE}
score_bar(df_long, "tmb_matching", "TMB: Matching")  
plot_within(df_long, "tmb_matching", "TMB: Matching - within")
plot_trend(df_long, "tmb_matching", "TMB: Matching - trend")
plot_within_sd(df_long, "tmb_matching", "TMB: Matching - within SD")
```

***
T17v4.

### **TMB: Difference**
```{r tmb-plots-4, eval=FALSE}
score_bar(df_long, "tmb_difference", "TMB: Difference")  
plot_within(df_long, "tmb_difference", "TMB: Difference - within")
plot_trend(df_long, "tmb_difference", "TMB: Difference - trend")
plot_within_sd(df_long, "tmb_difference", "TMB: Difference - within SD")
```