---
title: "Variability Check GMDD - part 1"
author: "Irene Xu"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: yeti
    code_folding: hide
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: true
      smooth_scroll: false
---

# 1. Load packages, Import data, Set style
```{r, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 10, fig.height = 20)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(Rmisc)
library(ggpubr)
library(EnvStats)

df_long <- read_csv("data/GMDD_TMB_long_2021-08-17.csv") %>%
  filter(!(visit %in% c("3t_mri", "4t_mri"))) %>%
  mutate(visit = as.numeric(visit))
```

***

# 2. Create functions
1. The first function plots a distribution histogram for each variable.
```{r score_bar}
score_bar <- function(data, var, vtitle, w = 1, a = 0.8) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = var, fill = arm)) + 
    geom_histogram(position = 'dodge2', alpha = a, binwidth = w) +
    theme_minimal() +
    labs(x = "", title = vtitle)
}
```

2. The second function plots the values by group.
```{r score_by_group}
score_group <- function(data, var, vtitle, s = 4, a = 0.6) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = arm, y = var, color = arm)) + 
    geom_jitter(size = s, alpha = a) +
    theme_bw() +
    theme(legend.position = "none") +
    labs(x = "", y = "", title = vtitle) +
    stat_n_text() 
}
```

3. The third function plots the values by group for each visit.
```{r score_by_visit}
score_by_visit <- function(data, var, vtitle, s = 0.5, a = 0.5) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(x = arm, y = var, color = arm)) + 
    geom_jitter(size = s, alpha = a) +
    theme_bw() +
    theme(legend.position = "none") +
    labs(title = vtitle, x = "", y = "") +
    stat_n_text(size = 2.8, vjust = -0.1) +
    facet_wrap(~visit, scales = "free")
}
```

4. The fourth function creates a line graph for each individual.
```{r plot_within}
plot_within <- function (data, fun.y, vtitle) {
  data$fun.y <- data[, fun.y]
  data$fun.y <- unlist(data$fun.y)
  ggplot(data, aes(as.numeric(visit), fun.y, group = record_id, color = record_id)) +
    geom_line(alpha = 0.6) +
    theme_bw() +
    theme(legend.position = "None") +
    labs(title = vtitle, subtitle = "by individial", x = "visit", y = "") +
    stat_n_text(size = 3, check_overlap = TRUE, angle = 25) 
}
```

5. The fifth function plots the mean for each visit for each group.
```{r trend_by_group}
trend_by_group <- function(data, fun.y, vtitle) {
  data$fun.y <- unlist(data[, fun.y])
  summary <- summarySE(data, measurevar = fun.y, groupvars = c("arm", "visit"), na.rm = TRUE)
  summary$fun.y = unlist(summary[, fun.y])
  ggplot(summary, aes(x = visit, y = fun.y, color = arm)) +
    geom_errorbar(aes(ymin = fun.y - se, ymax = fun.y + se), width = 0.4)+
    geom_line(position = position_dodge(-0.2)) +
    geom_point(size = 1.6, shape = 21, fill = "white", position = position_dodge(-0.2)) +
    labs(y = "", title = vtitle, subtitle = "by group") +
    theme_bw()
}
```

6. The sixth function plots the error bars for within-person variance by visit.
```{r within_by_visit}
plot_trend <- function(data, fun.y, vtitle) {
  data$fun.y <- unlist(data[, fun.y])
  SE_controlled <- summarySEwithin(data, measurevar = fun.y, 
                                   withinvars = "visit", idvar = "record_id", na.rm = TRUE)
  
  SE_controlled$fun.y = unlist(SE_controlled[, fun.y])
  
  ggplot(SE_controlled, aes(x = as.numeric(visit), y = fun.y)) +
    geom_line(color = "darkgrey") +
    geom_errorbar(aes(ymin = fun.y - se, ymax = fun.y + se), width = 0.4, color = "deepskyblue3") +
    geom_point(size = 2, shape = 21, color = "deepskyblue3", fill = "deepskyblue3") + 
    theme_bw(base_size = 12) +
    xlab("visit") +
    ylab("score") +
    ggtitle(vtitle, subtitle = "controlled for between-subject variance") +
    theme(legend.position = "none")
}
```

7. The seventh function takes in a helper function that returns the overall sd for a variable, plots the distribution of within-subject sd and plots the overall sd.
```{r plot_within_sd}
sd_all <- function(data, var) {
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd(data$var, na.rm = TRUE)
}

plot_within_sd <- function(data, var, vtitle) {
  sd_var <- sd_all(data, var)
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd_within_data <- data %>% group_by(record_id) %>% dplyr::summarize(sd = sd(var, na.rm = TRUE))
  ggplot(sd_within_data, aes(sd)) + geom_density(color = "deepskyblue4", fill = "deepskyblue4", alpha = 0.7) +
    geom_vline(data = data, xintercept = sd_var, color = "deepskyblue4") +
    theme_minimal() +
    labs(title = vtitle, subtitle = "area: within-person sd\nvertical line: within+between sd") 
}
```

8. The eighth function shows all 7 plots for each variable
```{r master-function}
plot_all <- function(var, vtitle, p1_width = 1, p1_alpha = 0.8, p2_size = 4, p2_alpha = 0.6, p3_size = 0.5, p3_alpha = 0.5) {
p1 <- score_bar(df_long, var, vtitle, p1_width, p1_alpha)
p2 <- score_group(df_long, var, vtitle, p2_size, p2_alpha)
p3 <- score_by_visit(df_long, var, vtitle, p3_size, p3_alpha)
p4 <- trend_by_group(df_long, var, vtitle)
p5 <- plot_trend(df_long, var, vtitle)
p6 <- plot_within(df_long, var, vtitle)
p7 <- plot_within_sd(df_long, var, vtitle)
lay <- rbind(c(1, 1, 1, 1, 1, 1, 2, 2, 2, 2),
             c(3, 3, 3, 3, 3, 3, 3, 3, 3, NA),
             c(3, 3, 3, 3, 3, 3, 3, 3, 3, NA),
             c(4, 4, 4, 4, 4, 5, 5, 5, 5, 5),
             c(6, 6, 6, 6, 6, 6, 7, 7, 7, 7))
grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix = lay)
}
```

***

# 3. Visualize the distribution of test scores

## **Test 1. VRT** checked
* Visual Reproduction Test
* baseline only
* variables: 3

T1v1.   

### **Immediate Recall**
```{r vrt-plots-1, fig.width = 5, fig.height = 4 }
score_bar(df_long, "vrt_ir_t_score", "Visual Reproduction Test: Immediate Recall (t)", 3)
score_group(df_long, "vrt_ir_t_score", "Visual Reproduction Test: Immediate Recall (t)", 4, 0.5)
```

***
T1v2.

### **Delayed Recall**
```{r vrt-plots-2, fig.width = 5, fig.height = 4 }
score_bar(df_long, "vrt_dr_t_score", "Visual Reproduction Test: Delayed Recall (t)", 3)
score_group(df_long, "vrt_dr_t_score", "Visual Reproduction Test: Delayed Recall (t)", 4, 0.5)
```

***
T1v3. 

### **Recognition Score**
```{r vrt-plots-3, fig.width = 5, fig.height = 4 }
score_bar(df_long, "vrt_rec_score", "Visual Reproduction Test: Recognition Score")
score_group(df_long, "vrt_rec_score", "Visual Reproduction Test: Recognition Score", 4, 0.5)
```

***

## **Test 2. CVLT-II** outliers
* California Verbal Learning Test  
* Mood: 1, 5, 9, 13, 14, 15
* Control: 1, 3, 4, 5, 6, 8
* variables: 8   

***
T2v1.

### **Immediate Free Recall**
```{r cvlt-plots-1 }
plot_all("cvlt_total_imfree_raw", "CVLT: Total Immediate Free Recall", 3, 0.8, 3, 0.3)
```

***
T2v2. 

### **Total Intrusions** 
```{r cvlt-plots-2 }
plot_all("cvlt_total_int_t", "CVLT: Total Intrusions", 3, 0.8, 3, 0.3)
```

***
T2v3.

### **Total Intrusions (Free Recall)** 
```{r cvlt-plots-3 }
plot_all("cvlt_total_free_int_t", "CVLT: Total Intrusions, free (t)", 4, 1, 3, 0.3)
```


***
T2v4.

### **Total Intrusions (Cued Recall)**
```{r cvlt-plots-4 }
df_long <- df_long %>%
  mutate(cvlt_total_cued_int_t = ifelse(cvlt_total_cued_int_t >= 600, NA, cvlt_total_cued_int_t))
plot_all("cvlt_total_cued_int_t", "CVLT: Total Intrusions, cued (t)", 4, 0.9, 3, 0.3)
```

***
T2v5. 

### **Total Recognition Target**
```{r cvlt-plots-5 }
plot_all("cvlt_total_rectarget_t", "CVLT: Total Recognition Target", 3, 0.8, 3, 0.3)
```

***
T2v6. 

### **Total Recognition Intrusions**
```{r cvlt-plots-6 }
plot_all("cvlt_total_rec_int_t", "CVLT: Total Recognition Intrusions (t)", 3, 0.8, 3, 0.3)
```

***
T2v7. 

### **Total Recognition Accuracy** outliers found
```{r cvlt-plots-7 }
plot_all("cvlt_total_rec_accuracy", "CVLT: Total Recognition Accuracy (t)", 3, 0.8, 3, 0.3)
```

***
T2v8. 

### **Total Repetition**
```{r cvlt-plots-8 }
plot_all("cvlt_total_rep_t", "CVLT: Total Repetition - (t)", 3, 0.8, 3, 0.3)
```

***

## **Test 3. VFT**     
* Verbal Fluency Test (aka. FAS)
* Mood: 1, 5, 9, 13, 14, 15
* Control: 1, 3, 4, 5, 6, 8
* variables: 2

***
T3v1.

### **Animals**
```{r vft-plots-1 }
plot_all("vft_animals", "VFT: Animals", 1, 0.8, 3, 0.3)
```

***
T3v2.

### **FAS**
```{r vft-plots-2 }
plot_all("vft_fas_raw", "VFT: FAS (raw)", 2, 0.8, 3, 0.3)
```

***

## **Test 4. Stroop** Identifiers of valid 0?
* Stroop Test
* Mood: 1, 5, 9, 13, 14, 15
* Control: 1, 3, 4, 5, 6, 8
* variables: 4

***
T4v1.

### **Word Deviation** 
```{r stroop-plots-1 }
plot_all("stroop_wscore_dev", "Stroop: word deviation", 2, 0.8, 3, 0.3)
```

***
T4v2.

### **Color Deviation**
```{r stroop-plots-2 }
plot_all("stroop_cscore_dev", "Stroop: color deviation", 2, 0.8, 3, 0.3)
```

***
T4v3.

### **Color Word Deviation**
```{r stroop-plots-3 }
plot_all("stroop_cwscore_dev_3", "Stroop: color word deviation", 1, 0.8, 3, 0.3)
```

***
T4v4.

### **Color Word**
```{r stroop-plots-4 }
plot_all("strop_cw_int_t", "Stroop: color word (t)", 1, 0.8, 3, 0.3)
```

***

## **Test 7. MMSE** outliers? Identifiers of valid 0?
* Mini-Mental State Exam
* baseline, v3, 5, 7, 9, 11, 13
* variables: 1

***
T7v1.

### **Total**
```{r mmse-plots-1 }
plot_all("mmse_total_score", "MMSE Total", 1, 0.8, 3, 0.2)
```

***

## **Test 9. WCST** (some data removed from redcap)
* Wisconsin Card Sort Task
* baseline
* variables: 5 included here (some unavailable)

***
T9v1.

### **Total Error - raw**
```{r wcst-plots-1, fig.width = 5, fig.height = 4 }
score_bar(df_long, "wcst_total_errors_raw", "WCST: Total Error - raw")
```

***
T9v2.

### **Perseverative Responses - raw**
```{r wcst-plots-2, fig.width = 5, fig.height = 4 }
score_bar(df_long, "wcst_pers_res_raw", "WCST: Perseverative Responses - raw", 3)
```

***
T9v3.

### **Perseverative Errors - raw**
```{r wcst-plots-3, fig.width = 5, fig.height = 4 }
score_bar(df_long, "wcst_pers_err_pct", "WCST: Perseverative Errors - raw", 3)
```

***
T9v4.

### **Non-Perseverative Errors - raw**
```{r wcst-plots-4, fig.width = 5, fig.height = 4 }
score_bar(df_long, "wcst_npers_err_raw", "WCST: Non-Perseverative Errors - raw")
```

***
T9v5.

### **Conceptual Level Responses - raw**
```{r wcst-plots-5, fig.width = 5, fig.height = 4 }
score_bar(df_long, "wcst_conc_raw", "WCST: Conceptual Level Responses - raw", 2)
```

***

## **Test 10. WTAR** outliers?
* Weschler Test of Adult Reading
* baseline
* variables: 1

***
T10v1.

### **Total**
```{r wtar-plots-1, fig.width = 5, fig.height = 4 }
score_bar(df_long, "wtar_raw_score", "WTAR: Total")
```

***

## **Test 11. MADRS** Identifiers of valid 0?
* Montgomery-Asberg Depression Rating Scale
* all visits
* variables: 11

***
T11v1.

### **Total**
```{r madrs-plots-1 }
plot_all("madrs_total", "MADRS: Total", 1, 0.8, 2, 0.2)  
```

***
T11v2.

### **Apparent Sadness**
```{r madrs-plots-2 }
plot_all("madrs_as_score", "MADRS: Apparent Sadness", 1, 0.8, 2, 0.2)
```

***
T11v3.

### **Reported Sadness**
```{r madrs-plots-3 }
plot_all("madrs_rs_score", "MADRS: Reported Sadness", 1, 0.8, 2, 0.2)
```

***
T11v4.

### **Inner Tension**
```{r madrs-plots-4 }
plot_all("madrs_it_score", "MADRS: Inner Tension", 1, 0.8, 2, 0.2)
```

***
T11v5.

### **Reduced Sleep**
```{r madrs-plots-5 }
plot_all("madrs_rs_score", "MADRS: Reduced Sleep", 1, 0.8, 2, 0.2)
```

***
T11v6.

### **Reduced Appetite**
```{r madrs-plots-6 }
plot_all("madrs_ra_score", "MADRS: Reduced Appetite", 1, 0.8, 2, 0.2)
```

***
T11v7.

### **Concentration Difficulties**
```{r madrs-plots-7 }
plot_all("madrs_cd_score", "MADRS: Concentration Difficulties", 1, 0.8, 2, 0.2)
```

***
T11v8.

### **Lassitude**
```{r madrs-plots-8 }
plot_all("madrs_las_score", "MADRS: Lassitude", 1, 0.8, 2, 0.2)
```

***
T11v9.

### **Inability to Feel**
```{r madrs-plots-9 }
plot_all("madrs_itf_score", "MADRS: Inability to Feel", 1, 0.8, 2, 0.2)
```

***
T11v10.

### **Pessimistic Thoughts**
```{r madrs-plots-10 }
plot_all("madrs_pt_score", "MADRS: Pessimistic Thoughts", 1, 0.8, 2, 0.2)
```

***
T11v11.

### **Suicidal Thoughts**
```{r madrs-plots-11 }
plot_all("madrs_st_score", "MADRS: Suicidal Thoughts", 1, 0.8, 2, 0.2)
```

***
## **Test 12. YMRS** Identifiers of valid 0?
* Young Mania Rating Scale
* all visits
* variables: 12

***
T12v1.

### **Total**
```{r ymrs-plots-1 }
plot_all("ymrs_total", "YMRS: Total", 1, 0.8, 2, 0.2)  
```

***
T12v2.

### **Elevated Mood**
```{r ymrs-plots-2 }
plot_all("ymrs_elevatedmood", "YMRS: Elevated Mood", 1, 0.8, 2, 0.2)  
```

***
T12v3.

### **Motor Activity**
```{r ymrs-plots-3 }
plot_all("ymrs_motoractivity", "YMRS: Motor Activity", 1, 0.8, 2, 0.2)  
```

***
T12v4.

### **Sex Interest**
```{r ymrs-plots-4 }
plot_all("ymrs_sexinterest", "YMRS: Sex Interest", 1, 0.8, 2, 0.2)  
```

***
T12v5.

### **Sleep**
```{r ymrs-plots-5 }
plot_all("ymrs_sleep", "YMRS: Sleep", 1, 0.8, 2, 0.2)  
```

***
T12v6.

### **Irritability**
```{r ymrs-plots-6 }
plot_all("ymrs_irritability", "YMRS: Irritability", 1, 0.8, 2, 0.2)  
```
***

T12v7.

### **Speech**
```{r ymrs-plots-7 }
plot_all("ymrs_speech", "YMRS: Speech", 1, 0.8, 2, 0.2)  
```

***
T12v8.

### **Language**
```{r ymrs-plots-8 }
plot_all("ymrs_language", "YMRS: Language", 1, 0.8, 2, 0.2)  
```

***
T12v9.

### **Content**
```{r ymrs-plots-9 }
plot_all("ymrs_content", "YMRS: Content", 1, 0.8, 2, 0.2)  
```

***
T12v10.

### **Disruptive**
```{r ymrs-plots-10 }
plot_all("ymrs_disruptive", "YMRS: Disruptive", 1, 0.8, 2, 0.2)  
```

***
T12v11.

### **Appearance**
```{r ymrs-plots-11 }
plot_all("ymrs_appearance", "YMRS: Appearance", 1, 0.8, 2, 0.2)  
```

***
T12v12.

### **Insight**
```{r ymrs-plots-12 }
plot_all("ymrs_insight", "YMRS: Insight", 1, 0.8, 2, 0.2)  
```

***
## **Test 13. GAF** checked
* Global Assessment of Functioning
* all visits
* variables: 1

***
T13v1.

### **Score**
```{r gaf-plots-1, fig.width = 7, fig.height = 4 }
score_bar(df_long, "gaf_score", "GAF: Score", 2)  
```

***
## **Test 14. IGT** checked
* Iowa Gambling Task
* baseline, 5, 9, 13
* variables: 11

***
T14v1.

### **Net Total**
```{r igt-plots-1 }
plot_all("igt_net_total_t", "IGT: Net Total (t)", 2, 0.8, 3, 0.3)  
```

***
T14v2.

### **Net part 1 (t value)**
```{r igt-plots-2 }
plot_all("igt_net_1_t", "IGT: Net part 1 (t)", 2, 0.8, 3, 0.3)  
```

***
T14v3.

### **Net part 2 (t value)**
```{r igt-plots-3 }
plot_all("igt_net_2_t", "IGT: Net part 2 (t)", 2, 0.8, 3, 0.3)  
```

***
T14v4.

### **Net part 3 (t value)**
```{r igt-plots-4 }
plot_all("igt_net_3_t", "IGT: Net part 3 (t)", 1.5, 0.8, 3, 0.3)  
```

***
T14v5.

### **Net part 4 (t value)**
```{r igt-plots-5 }
plot_all("igt_net_4_t", "IGT: Net part 4 (t)", 1.5, 0.8, 3, 0.3)  
```

***
T14v6.

### **Net part 5 (t value)**
```{r igt-plots-6 }
plot_all("igt_net_5_t", "IGT: Net part 5 (t)", 1, 0.8, 3, 0.3)  
```

***
T14v7.

### **Deck A**
```{r igt-plots-7 }
plot_all("igt_deck_a", "IGT: Deck A", 1.5, 0.8, 3, 0.3)  
```

***
T14v8.

### **Deck B**
```{r igt-plots-8 }
plot_all("igt_deck_b", "IGT: Deck B", 1.5, 0.8, 3, 0.3)  
```

***
T14v9.

### **Deck C**
```{r igt-plots-9 }
plot_all("igt_deck_c", "IGT: Deck C", 1, 0.8, 3, 0.3)  
```

***
T14v10.

### **Deck D**
```{r igt-plots-10 }
plot_all("igt_deck_d", "IGT: Deck D", 2, 0.8, 3, 0.3)  
```

***
T14v11.

### **Total money**
```{r igt-plots-11 }  
plot_all("igt_total_money", "IGT: Total money", 75, 0.8, 3, 0.3)  
```

***

***

## **Test 15. VOSP** gap?
* Visual Object and Space Perception: Shape Detection
* baseline, 5, 9, 13
* variables: 1

***
T15v1.

### **Total**
```{r vosp-plots-1, fig.width = 5, fig.height = 4 }
score_bar(df_long, "vosp_total", "VOSP: Total")  
```

***

## **Test 16. MITE** Identifiers of valid 0?
* Mind in the Eyes
* baseline, 5, 9, 13
* variables: 2

***
T16v1.

### **Correct**
```{r mite-plots-1 }
plot_all("mind_eyes_correct", "MITE: Correct", 1, 1, 2.5, 0.25)  
```

***
T16v2.

### **t - value**
```{r mite-plots-2 }
plot_all("mind_eyes_t", "MITE: t value", 1, 1, 2.5, 0.25)  
```
