---
title: "Variability Check (part 2)"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: yeti
    code_folding: hide
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: true
      smooth_scroll: true
---
# 1. Load packages, Import data, Set style
```{r, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 5, fig.height = 4)

library(tidyverse)
library(ggplot2)
library(Rmisc)
library(ggpubr)

df_long <- read_csv("data/GMDD_TMB_long_2021-08-17.csv") %>%
  filter(!(visit %in% c("3t_mri", "4t_mri"))) %>%
  mutate(visit = as.numeric(visit))
```

***

# 2. Create functions
```{r plot_score}
## this function plots a distribution histogram for each variable ********
plot_score <- function(data, var, vtitle) {
  data$var <- unlist(data[, var])
  ggplot(data, aes(var)) + 
    geom_bar() +
    theme_minimal() +
    xlab("") +
    ggtitle(vtitle)
}

## this function creates a line graph for each individual ****************
plot_within <- function (data, fun.y, vtitle) {
  data$fun.y <- data[, fun.y]
  data$fun.y <- unlist(data$fun.y)
  ggplot(data, aes(as.numeric(visit), fun.y, group = record_id, color = record_id)) +
    geom_line(alpha = 0.4) +
#    geom_point(SIZE = 0.5, alpha = 0.4) +
    theme_classic(base_size = 12) +
    theme(legend.position = "None") +
    labs(title = vtitle)  +
    ylab("") +
    xlab("visit")
}

## this function returns the overall sd for a variable *****************
sd_all <- function(data, var) {
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd(data$var, na.rm = TRUE)
}

# this function plots the distribution of within-subject sd for a variable, 
# and also plots the overall sd ****************************************
plot_within_sd <- function(data, var, vtitle) {
  sd_var <- sd_all(data, var)
  data$var <- data[, var]
  data$var <- unlist(data$var)
  sd_within_data <- data %>% group_by(record_id) %>% dplyr::summarize(sd = sd(var, na.rm = TRUE))
  ggplot(sd_within_data, aes(sd)) + geom_density(fill = "lightgrey") +
    geom_vline(data = data, xintercept = sd_var) +
    theme_minimal() +
    ggtitle(vtitle) 
}

# this function plots the error bars for within-person variance by visit ********
plot_trend <- function(data, fun.y, vtitle) {
  data$fun.y <- unlist(data[, fun.y])
  SE_controlled <- summarySEwithin(data, measurevar = fun.y, 
                                   withinvars = "visit", idvar = "record_id", na.rm = TRUE)
  
  SE_controlled$fun.y = unlist(SE_controlled[, fun.y])
  
  ggplot(SE_controlled, aes(x = as.numeric(visit), y = fun.y, color = visit)) +
    geom_line(color = "grey") +
    geom_errorbar(aes(ymin = fun.y - se, ymax = fun.y + se), width = 0.4) +
    geom_point(size = 2) + 
    theme_classic(base_size = 12) +
    xlab("visit") +
    ylab("score") +
    ggtitle(vtitle, subtitle = "controlled for between-subject variance") +
    theme(legend.position = "none")
}
```

***

# 3. Visualize the distribution of test scores
## **Test 18. CGI-S**
* Clinical Global Impression: Severity
* 1, 3, 5, 7, 9, 11, 13
* variables: 1

***
T18v1.   

### **CGI-S**
```{r cgis-plots-1}
plot_score("cgi_s", "CGI-S")
plot_within(df_long, "cgi_s", "CGI-S - within")
plot_within_sd(df_long, "cgi_s", "CGI-S - within SD")
```

***

## **Test 19. CIRS-G**
* Cumulative Illness Rating Scale - Geriatrics
* 1, 5, 9, 13
* variables: 4

***
T19v1.   

### **CIRS-G: Total**
```{r cirsg-plots-1}
plot_score("cirsg_total_score", "CIRS-G: Total")
plot_within(df_long, "cirsg_total_score", "CIRS-G: Total - within")
plot_within_sd(df_long, "cirsg_total_score", "CIRS-G: Total - within SD")
```

***
T19v2.   

### **CIRS-G: Severity Index**
```{r cirsg-plots-2}
plot_score("cirsg_severity_index", "CIRS-G: Severity Index")
plot_within(df_long, "cirsg_severity_index", "CIRS-G: Severity Index - within")
plot_within_sd(df_long, "cirsg_severity_index", "CIRS-G: Severity Index - within SD")
```

***
T19v3.   

### **CIRS-G: Level 3 severity**
```{r cirsg-plots-3}
plot_score("cirsg_level3_severity", "CIRS-G: Level 3 severity")
plot_within(df_long, "cirsg_level3_severity", "CIRS-G: Level 3 severity - within")
plot_within_sd(df_long, "cirsg_level3_severity", "CIRS-G: Level 3 severity - within SD")
```

***
T19v4.   

### **CIRS-G: Level 4 severity**
```{r cirsg-plots-4}
plot_score("cirsg_level4_severity", "CIRS-G: Level 4 severity")
plot_within(df_long, "cirsg_level4_severity", "CIRS-G: Level 4 severity - within")
plot_within_sd(df_long, "cirsg_level4_severity", "CIRS-G: Level 4 severity - within SD")
```

***

## **Test 20. SRFPC**
* Stroke Risk Factor Prediction Chart
* 1, 5, 9, 13
* variables: 1

***
T20v1.   

### **SRFPC: Total**
```{r srfpc-plots-1}
plot_score("srfpc_total", "SRFPC: Total")
plot_within(df_long, "srfpc_total", "SRFPC: Total - within")
plot_within_sd(df_long, "srfpc_total", "SRFPC: Total - within SD")
```

***

## **Test 21. Social Perception**
* Social Perception
* 1, 5, 9, 13
* variables: 3

***
T21v1.   

### **Social Perception: Affect Naming Total**
```{r sp-plots-1}
plot_score("affect_naming_total", "Social Perception: Affect Naming Total")
plot_within(df_long, "affect_naming_total", "Social Perception: Affect Naming Total - within")
plot_within_sd(df_long, "affect_naming_total", "Social Perception: Affect Naming Total - within SD")
```

***
T21v2.   

### **Social Perception: Affect Naming Scaled**
```{r sp-plots-2}
plot_score("affect_naming_scaled", "Social Perception: Affect Naming Scaled")
plot_within(df_long, "affect_naming_scaled", "Social Perception: Affect Naming Scaled - within")
plot_within_sd(df_long, "affect_naming_scaled", "Social Perception: Affect Naming Scaled - within SD")
```

***
T21v3.   

### **Social Perception: Affect Naming - t value**
```{r sp-plots-3}
plot_score("affect_naming_t", "Social Perception: Affect Naming - t value")
plot_within(df_long, "affect_naming_t", "Social Perception: Affect Naming - t value - within")
plot_within_sd(df_long, "affect_naming_t", "Social Perception: Affect Naming - t value - within SD")
```

***

## **Test 22. CERAD Neuropsych Battery**
* Social Perception
* 1, 5, 9, 13
* variables: 4

***
T22v1.   

### **CERAD:  BNT Boston Naming test Total**
```{r cerad-plots-1}
plot_score("cerad_bnt_total", "BNT Total")
plot_within(df_long, "cerad_bnt_total", "BNT Total - within")
plot_within_sd(df_long, "cerad_bnt_total", "BNT Total - within SD")
```

***
T22v2.   

### **CERAD: Constructional Praxis Total**
```{r cerad-plots-2}
plot_score("cerad_cp_total", "Constructional Praxis Total")
plot_within(df_long, "cerad_cp_total", "Constructional Praxis Total - within")
plot_within_sd(df_long, "cerad_cp_total", "Constructional Praxis Total - within SD")
```

***
T22v3.   

### **CERAD: Word List Recognition Total**
```{r cerad-plots-3}
plot_score("cerad_wlrec_total", "Word List Recognition Total")
plot_within(df_long, "cerad_wlrec_total", "Word List Recognition Total - within")
plot_within_sd(df_long, "cerad_wlrec_total", "Word List Recognition Total - within SD")
```

***
T22v4.   

### **CERAD: Constructional Praxis Recall Total**
```{r cerad-plots-4}
plot_score("cerad_cpr_total", "Constructional Praxis Recall Total")
plot_within(df_long, "cerad_cpr_total", "Constructional Praxis Recall Total - within")
plot_within_sd(df_long, "cerad_cpr_total", "Constructional Praxis Recall Total - within SD")
```

*** 

## **Test 23. Go-No Go**
* Go-No Go
* 1, 5, 9, 13
* variables: 2

***
T23v1.   

### **GNG: Conflict**
```{r gng-plots-1}
plot_score("gng_conflict", "GNG: Conflict")
plot_within(df_long, "gng_conflict", "GNG: Conflict - within")
plot_within_sd(df_long, "gng_conflict", "GNG: Conflict - within SD")
```

***
T23v2.

### **GNG: Inhibit**
```{r gng-plots-2}
plot_score("gng_inhibit", "GNG: Inhibit")
plot_within(df_long, "gng_inhibit", "GNG: Inhibit - within")
plot_within_sd(df_long, "gng_inhibit", "GNG: Inhibit - within SD")
```

*** 

## **Test 24. PANAS**
* Positive And Negative Affect Schedule
* all visits
* variables: 2

***
T24v1.   

### **PANAS: Positive**
```{r panas-plots-1}
plot_score("panas_positive", "PANAS: Positive")
plot_within(df_long, "panas_positive", "PANAS: Positive - within")
plot_within_sd(df_long, "panas_positive", "PANAS: Positive - within SD")
```

***
T24v2.   

### **PANAS: Negative**
```{r panas-plots-2}
plot_score("panas_negative", "PANAS: Negative")
plot_within(df_long, "panas_negative", "PANAS: Negative - within")
plot_within_sd(df_long, "panas_negative", "PANAS: Negative - within SD")
```

*** 

## **Test 25. GDS**
* Geriatric Depression Scale
* all visits
* variables: 1

***
T25v1.   

### **GDS: Total**
```{r gds-plots-1}
plot_score("gds_total", "GDS: Total")
plot_within(df_long, "gds_total", "GDS: Total - within")
plot_within_sd(df_long, "gds_total", "GDS: Total - within SD")
```

*** 

## **Test 26. GAD-7**
* Geriatric Depression Scale
* all visits
* variables: 2

***
T26v1.   

### **GAD-7: Total**
```{r gad-plots-1}
plot_score("gad_total", "GAD: Total")
plot_within(df_long, "gad_total", "GAD: Total - within")
plot_within_sd(df_long, "gad_total", "GAD: Total - within SD")
```

***
T26v2.   

### **GAD-7: Difficulty**
```{r gad-plots-2}
plot_score("gad_difficulty", "GAD: Difficulty")
plot_within(df_long, "gad_difficulty", "GAD: Difficulty - within")
plot_within_sd(df_long, "gad_difficulty", "GAD: Difficulty - within SD")
```

*** 

## **Test 27. WHODAS**
* WHODAS
* 1, 3, 5, 7, 9, 11, 13
* variables: 1

***
T27v1.   

### **WHODAS: sum**
```{r whodas-plots-1}
plot_score("whodas_s_sum", "WHODAS: Sum")
plot_within(df_long, "whodas_s_sum", "WHODAS: Sum - within")
plot_within_sd(df_long, "whodas_s_sum", "WHODAS: Sum - within SD")
```

*** 

## **Test 28. FAST-ER**
* FAST-ER
* all visits
* variables: 1

***
T28v1.   

### **FAST-ER: Total**
```{r faster-plots-1}
plot_score("faster_total", "FAST-ER: Total")
plot_within(df_long, "faster_total", "FAST-ER: Total - within")
plot_within_sd(df_long, "faster_total", "FAST-ER: Total - within SD")
```

*** 

## **Test 29. FAS-D**
* Fatigue Associated with Depression
* all visits
* variables: 3

***
T29v1.   

### **FAS-D: Total **
```{r fasd-plots-1}
plot_score("fasd_total", "FAS-D: Total")
plot_within(df_long, "fasd_total", "FAS-D: Total - within")
plot_within_sd(df_long, "fasd_total", "FAS-D: Total - within SD")
```

***
T29v2.   

### **FAS-D: Total Experience**
```{r fasd-plots-2}
plot_score("fasd_total_experience", "FAS-D: Total Experience")
plot_within(df_long, "fasd_total_experience", "FAS-D: Total Experience - within")
plot_within_sd(df_long, "fasd_total_experience", "FAS-D: Total Experience - within SD")
```

***
T29v3.   

### **FAS-D: Total Impact**
```{r fasd-plots-3}
plot_score("fasd_total_impact", "FAS-D: Total Impact")
plot_within(df_long, "fasd_total_impact", "FAS-D: Total Impact - within")
plot_within_sd(df_long, "fasd_total_impact", "FAS-D: Total Impact - within SD")
```

*** 

## **Test 30. Spirituality**
* Spirituality
* 1, 3, 5, 7, 9, 11, 13
* variables: 6

***
T30v1.   

### **Spirituality I: Total**
```{r spirituality-plots-1}
plot_score("spirituality_i_total", "Spirituality I: Total")
plot_within(df_long, "spirituality_i_total", "Spirituality I: Total - within")
plot_within_sd(df_long, "spirituality_i_total", "Spirituality I: Total - within SD")
```

***
T30v2.   

### **Spirituality II: Trust**
```{r spirituality-plots-2}
plot_score("spirituality_ii_trust", "Spirituality II: Trust")
plot_within(df_long, "spirituality_ii_trust", "Spirituality II: Trust - within")
plot_within_sd(df_long, "spirituality_ii_trust", "Spirituality II: Trust - within SD")
```

***
T30v3.   

### **Spirituality II: Mistrust**
```{r spirituality-plots-3}
plot_score("spirituality_ii_mistrust", "Spirituality II: Mistrust")
plot_within(df_long, "spirituality_ii_mistrust", "Spirituality II: Mistrust - within")
plot_within_sd(df_long, "spirituality_ii_mistrust", "Spirituality II: Mistrust - within SD")
```

***
T30v4.   

### **Spirituality III: Total**
```{r spirituality-plots-4}
plot_score("spirituality_iii_total", "Spirituality III: Total")
plot_within(df_long, "spirituality_iii_total", "Spirituality III: Total - within")
plot_within_sd(df_long, "spirituality_iii_total", "Spirituality III: Total - within SD")
```

***
T30v5.   

### **Spirituality IV: Positive**
```{r spirituality-plots-5}
plot_score("spitituality_iv_positive", "Spirituality IV: Positive")
plot_within(df_long, "spitituality_iv_positive", "Spirituality IV: Positive - within")
plot_within_sd(df_long, "spitituality_iv_positive", "Spirituality IV: Positive - within SD")
```

***
T30v6.   

### **Spirituality IV: Negative**
```{r spirituality-plots-6}
plot_score("spitituality_iv_negative", "Spirituality IV: Negative")
plot_within(df_long, "spitituality_iv_negative", "Spirituality IV: Negative - within")
plot_within_sd(df_long, "spitituality_iv_negative", "Spirituality IV: Negative - within SD")
```

*** 

## **Test 31. GAS**
* Geriatric Anxiety Scale
* all visits
* variables: 4

***
T31v1.   

### **GAS: Total**
```{r gas-plots-1}
plot_score("gas_total", "GAS: Total")
plot_within(df_long, "gas_total", "GAS: Total - within")
plot_within_sd(df_long, "gas_total", "GAS: Total - within SD")
```

***
T31v2.   

### **GAS: Somatic**
```{r gas-plots-2}
plot_score("gas_somatic", "GAS: Somatic")
plot_within(df_long, "gas_somatic", "GAS: Somatic - within")
plot_within_sd(df_long, "gas_somatic", "GAS: Somatic - within SD")
```

***
T31v3.   

### **GAS: Cognitive**
```{r gas-plots-3}
plot_score("gas_cognitive", "GAS: Cognitive")
plot_within(df_long, "gas_cognitive", "GAS: Cognitive - within")
plot_within_sd(df_long, "gas_cognitive", "GAS: Cognitive - within SD")
```

***
T31v4.

### **GAS: Affective**
```{r gas-plots-4}
plot_score("gas_affective", "GAS: Affective")
plot_within(df_long, "gas_affective", "GAS: Affective - within")
plot_within_sd(df_long, "gas_affective", "GAS: Affective - within SD")
```

*** 

## **Test 32. PSQI**
* Pittsburgh Sleep Quality Index
* all visits
* variables: 1

***
T32v1.   

### **PSQI: Total**
```{r psqi-plots-1}
plot_score("psqi_global_score", "PSQI: Total")
plot_within(df_long, "psqi_global_score", "PSQI: Total - within")
plot_within_sd(df_long, "psqi_global_score", "PSQI: Total - within SD")
```

*** 

## **Test 33. PAI SCZ**
* Personality Assessment Psychosis Subscale
* 1, 5, 9, 13
* variables: 4

***
T33v1.   

### **PAI SCZ: Total (t value)**
```{r paiscz-plots-1}
plot_score("pai_scz_total_t", "PAI SCZ: Total (t value)")
plot_within(df_long, "pai_scz_total_t", "PAI SCZ: Total (t value) - within")
plot_within_sd(df_long, "pai_scz_total_t", "PAI SCZ: Total (t value) - within SD")
```

***
T33v2.   

### **PAI SCZ: Psychotic Experiences (t value)**
```{r paiscz-plots-2}
plot_score("pai_scz_psychexp_t", "PAI SCZ: Psychotic Experiences (t value)")
plot_within(df_long, "pai_scz_psychexp_t", "PAI SCZ: Psychotic Experiences (t value) - within")
plot_within_sd(df_long, "pai_scz_psychexp_t", "PAI SCZ: Psychotic Experiences (t value) - within SD")
```

***
T33v3.   

### **PAI SCZ: Thought Disorder (t value)**
```{r paiscz-plots-3}
plot_score("pai_scz_thought_t", "PAI SCZ: Thought Disorder (t value)")
plot_within(df_long, "pai_scz_thought_t", "PAI SCZ: Thought Disorder (t value) - within")
plot_within_sd(df_long, "pai_scz_thought_t", "PAI SCZ: Thought Disorder (t value) - within SD")
```

***
T33v4.   

### **PAI SCZ: Social Detachment (t value)**
```{r paiscz-plots-4}
plot_score("pai_scz_social_t", "PAI SCZ: Social Detachment (t value)")
plot_within(df_long, "pai_scz_social_t", "PAI SCZ: Social Detachment (t value) - within")
plot_within_sd(df_long, "pai_scz_social_t", "PAI SCZ: Social Detachment (t value) - within SD")
```

*** 

## **Test 34. MMQ**
* Multi-factorial Memory Questionnaire
* 1, 5, 9, 13
* variables: 1

***
T34v1.   

### **MMQ: Total**
```{r mmq-plots-1}
plot_score("mmq_total", "MMQ: Total")
plot_within(df_long, "mmq_total", "MMQ: Total - within")
plot_within_sd(df_long, "mmq_total", "MMQ: Total - within SD")
```